### 2015-04-07 Bug_Insertion.tex
adding tex file

\documentclass[a4paper]{article}
%\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{url}
%\usepackage{html}
%\usepackage{hthtml}
\usepackage{geometry}

% Comments (optional argument is author of comment)
\newcommand{\comments}[2][?]{
  \begin{quote}
    \textbf{Comment (#1):} {\em #2}
  \end{quote}
  }

% \name is for ``special names'', like procedure or variable names.
\newcommand{\name}[1]{\texttt{\hturl{#1}}}

% Just a shortcut for links where the url appears as footnote.
\newcommand{\htflink}[2]{\htmladdnormallinkfoot{#1}{#2}}

\title{Bug Insertion}
\author{Gema Rodríguez Pérez}
\date{}

\sloppy
\begin{document}
\maketitle

\begin{abstract}
The objective of this paper is to prove that the bug can be not caused by the previous commit. Currently, the premise establishes that all the bugs were introduced by the previous commit. We have carried out an experiment which has helped us show results pointing out a minor disagreement with the present premise. We have observed three stages totally separable throughout the execution of this experiment. The first stage considers a classification, based on our knowledge of the ticket, in three groups: 
 1.It is an error. 
 2.It is not an error. 
 3.Unknown. 
 The second stage involves the analysis of it as an error. In this stage where, with some parameters of interest, we are able to give a percentage of how many prior commits were responsible for the bug. 
The third stage is the implementation of an analytic tool to help us with the first and second stages. 
In this paper we focus in two first stages. Explaining clearly and concisely the methodology used in our experiment.

\end{abstract}

\section{The experiment}

Our experiment consisted of the analysis of one hundred tickets which were taken randomly from Cinder repository. We will call the first stage ‘the filtering’ as we will classify them into three categories:

\begin{enumerate}
    \item It is an error.
    \item It is not an error.
    \item Unknown
\end{enumerate}

Two different people with knowledge about programming were responsible for classifying these tickets in accordance with their opinion of the three categories mentioned above. The two people worked in parallel during the filtering. Only when all the tickets were classified were both classifications compared. Those whose classification were different, were compared with each other, thus reaching an agreed classification. 
After filtering, we continued to the next stage, in which we only kept in mind those tickets belonging to ’It is an error’ group. In this phase we were able to conclude whether the bug was added in an earlier commit, or by contrast, if it was not. This stage is still being validated on account of a shortage of tickets analyzed. At this moment, we can design an efficient algorithm that involves relevant parameters to reach the conclusion that we are looking for. So, for the moment, we are using these parameters as a support.

\section{Several questions we have to answer}

To provide a context, we have to answer some questions referring to the project from which we have taken the information. Likewise, we are going to describe the specific vocabulary.
\begin{itemize}
\item What is OpenStack?

It is a combination of software tools for building and managing cloud computing platforms for public and private clouds. Principally, users deploy it as an infrastructure as a service (IaaS) solution. The technology consists of many different moving parts. In particular, OpenStack has nine key components that can be identified as part of the ”core”. Officially, OpenStack community maintained these system.

\begin{itemize}
    \item Compute (Nova) is the primary engine of an IaaS system. It is used for deploying and managing virtual machines.
    \item Object Storage (Swift) is a scalable redundant storage system for objects and files.
    \item Block Storage (Cinder) manages the creation, attaching and detaching of the block devices to servers, being able to access specific locations on a disk drive.
    \item Networking (Neutron) provides the networking capability for OpenStack managing IP addresses.
    \item Dashboard (Horizon) is the only graphical interface to OpenStack whereby administrators gain graphical access.
    \item Identity (Keystone) provides a central directory of users mapped to the OpenStack services that administrators and users can access.
    \item  Image Service (Glance) provides virtual copies of services to OpenStack. It allows use of these images as templates when deploying new virtual machine instances. 
    \item Telemetry Service (Ceilometer) 
    \item Orchestration (Heat) helps to manage the infrastructure needed for a cloud service to run through both a REST API and a Query API.
\end{itemize}

Each one of the above has its own API to achieve integration. Furthermore, all of them have a repository where the community implements improvements; fixing bugs ... etc.

\item How can OpenStack help us?

OpenStack is is of an open nature, anyone can add additional components to OpenStack to help it to meet their needs. Because of the high scope of OpenStack we have at our disposal several bugs that we are interested in. The first of which is in Cinder.

\item What is Cinder in OpenStack?

Cinder is a component of OpenStack, it works as a Block Storage manipulating volumes and snapshots. Cinder has a Data Base in which the state of each volume can be found.
At the same time, Cinder is composed of:

\begin{itemize}
    \item Cinder API: Accepts orders and routes them to cinder volume.
    \item Cinder Volume: Reacts to these requests, writing or reading the database. Furthermore, it interacts with other processes such as cinder Scheduler through the message queue. Also acts directly upon storage, providing hardware or software.
    \item Cinder Schedule: Selects the node to storage and volume where created.
\end{itemize}

\item What would we like to achieve by analyzing this repository?

Analyzing Cinder repository we would like obtain a percentage of how many errors have been inserted by the previous commit. Owing to the fact that the actual premise assumes that the error was introduced by previos commit.
It is important to be able to demonstrate that existing others factors contribute to the appearance of these errors.

\item What do we have to analyze in this repository

We need to be able to analyze a set of true tickets which will help us to reach the desired conclusion. Firstly, we have chosen a repository from Cinder, where we can find a wide group of tickets. These tickets have a state of progress, it is an updating of its status from opening the ticket until closing.  We only are interested in closed ticket and its releas patch,  that is, whose status is “Fix released” or “Fix Commited”.
Before reaching the goal, we have to answer intermediate questions which provide us with information throughout the analysis. 
First of all, we must be clear in what we will analyze and where we can find the necessary data for this analysis. So, the first questions are:

\item What is a ticket?

We call a ticket each of the entries that are published in \url{https://bugs.launchpad.net/cinder}, describing a bug. The purpose is to leave a written a evolution of the bug from its opening until it is fixed.

\item Where will we find a ticket?

The ticket are found in \url{https://bugs.launchpad.net/cinder}, where we must do an advanced search with a main search parameter called ”status" as:
\begin{itemize}
    \item Fix Committed: the changes are pending, and to be uploaded soon.
    \item Fix Released: a fix was uploaded to an official Cinder repository.
\end{itemize}

The next stage is to choose a random ticket and analyze it. Trying to answer the following questions until arriving at our objective. To answer the main questions, from the first level; we need to ask questions at the second level.
The main questions are:
\begin{itemize}
    \item Is it a Bug?
    \item Can we identify the commit responsible for the bug?
    \item Is the previous commit responsible?
\end{itemize}

As we have mentioned before, to answer the main questions we need to answer other questions like the following:

\item What do the title, the description and the commits of a ticket represent?

Once determined, we choose a ticket, we must to read carefully the title and the description of the ticket as well as the title of the commit which fixed the patch, because this is where will obtain more information from.

The title and the description of the ticket whose id is 'n\_ticket' can be found in \url{https://bugs.launchpad.net/cinder/+bug/n_ticket}. The title of the commit can, sometimes be found in the same link under the comment “Fix merged to cinder (master)”, where we can find link leads to the review of the ticket \url{https://review.openstack.org/#/c/n_review}. In the review all the information about the patch that fixed the bug is shown.

After analyzing these three fields,  we should note the keywords of each of them, because in our opinion, they will help us in the future to develop an algorithm. Understanding keywords as those words that show the same pattern or are specific will help us with the classification. In addition, very often (We must calculate the percentage from the experiment), the description helps us to answer the question: Is it a bug?.

At this stage, we are almost ready to answer the first question, Is it a bug?, Before that, we must be clear about the criteria that we will use.

\item What criteria will be used?

We need to define certain criteria that must be followed in case of doubt about it being a bug or not. We have based the answer on the following criteria:

\begin{itemize}
    \item Are there only test files?
    It is not an error. Our criteria indicate that test files will not be analyzed because we consider these files indispensable when a feature is implemented. With a test file the working order of the program is checked, in a way to give consistency to the program. A bug in the code, implicates there being a bug in the test file, provided that the test are implemented. So, we are not interested in these files.
    \item Does the title of  the ticket describe a new feature?
It is not an error. New features are not considered errors, because there is no failure. The optimization, deletion of a dead code or new characteristics to users are involved here.
    \item Does the title of the ticket describe the program as not working as expected?
It is an error. Sometimes the error is not in a main function which prevents Cinder from working, because a developer has considered it  an important error, although not relatively important. But it is not working as he/she expected.
    \item Does the title of the ticket describe that updates are required?
It is an error.  We consider all tickets that require updating as errors, because if it is not updating  cinder is not operating as expected and will cause errors.
\end{itemize}

Sometimes we are unable to answer all the questions due to having insufficient data or because of the complexity of the issue.

At this time, we should be able to classify the tickets according to their nature as:
\begin{enumerate}
    \item It is an error.
    \item It is not an error.
    \item Unknown
\end{enumerate}

In the experiment, we only have focused in the ‘It is an error’ group, as this is the ticket group that interests us.

Now the more difficult part begins. Commits will be focused on,  having to identify which lines have been removed, modified or added in each of them. Also we should know in which files are the answers to the question about who is responsible.

As before, to answer these questions we need to answer some questions from lower levels:

Sometimes, after having read the description of the ticket, we know if the ticket is an upgrade error. In this case, the answer to the question Is there a bug responsible? is negative. That is, according to our criteria nobody is responsible for the evolution of the code. Therefore, if an update is necessary, despite being an error there is no commit responsible for the  bug.

In other cases, after the description we can conclude that we are unable to identify a responsible commit, because the ticket includes more than one component within OpenStack and although it has been opened in Cinder could have been closed in another repository that belongs to another component of OpenStack. Therefore we do not have a review where we analyze the code and identify the commit responsible.

If the ticket is not in any of the above situations, we must be able to answer the next questions by analyzing the code of the files. These codes can be found in the review page of each ticket.  If you click on the file involved,  a comparison between the status of the file before commit and the status of the file after the commit appears.

\item What kind of code is it?

\item What number of commits are involved?

\item What will happen if the number of folders is greater than one?

\item Is it only the previous commit that is involved?

\item Is this the commit responsible?
\end{itemize}

\section{The results}

\section{Conclusions}

\end{document}

### 2015-04-16 Bug_Insertion.tex
adding Latex files

@@
 \begin{abstract}
-The objective of this paper is to prove that the bug can be not caused by the previous commit.
-Currently, the premise establishes that all the bugs were introduced by the previous commit.
+The objective of this paper is to prove that a bug is not caused by the previous commit.
+Currently, the premise establishes that all bugs were introduced by a previous commit.
 We have carried out an experiment which has helped us show results pointing out a minor disagreement with the present premise.
 We have observed three stages totally separable throughout the execution of this experiment.
-The first stage considers a classification, based on our knowledge of the ticket, in three groups:
+The first stage considers a classification, based on our knowledge of the ticket we have analysed, in three groups:
  1.It is an error. 
@@
 In this stage where, with some parameters of interest, we are able to give a percentage of how many prior commits were responsible for the bug.
-The third stage is the implementation of an analytic tool to help us with the first and second stages. 
+The third stage is the implementation of an analytical tool to help us with the first and second stages. 
 In this paper we focus in two first stages. Explaining clearly and concisely the methodology used in our experiment.
@@
 Our experiment consisted of the analysis of one hundred tickets which were taken randomly from Cinder repository.
-We will call the first stage ‘the filtering’ as we will classify them into three categories:
+We will call the first stage 'the filtering' as we will classify them into three categories:
 
@@
 
-Two different people with knowledge about programming were responsible for classifying these tickets in accordance with their opinion of the three categories mentioned above.
-The two people worked in parallel during the filtering.
+Two different people with knowledge of programming were responsible for classifying these tickets in accordance with their opinion of the three categories mentioned above.
+These two people worked in parallel during the filtering.
 Only when all the tickets were classified were both classifications compared.
 Those whose classification were different, were compared with each other, thus reaching an agreed classification.
-After filtering, we continued to the next stage, in which we only kept in mind those tickets belonging to ’It is an error’ group.
+
+After filtering, we continued to the next stage, in which we only kept in mind those tickets belonging to 'It is an error' group.
 In this phase we were able to conclude whether the bug was added in an earlier commit, or by contrast, if it was not.
@@
 To provide a context, we have to answer some questions referring to the project from which we have taken the information. Likewise, we are going to describe the specific vocabulary.
+
 \begin{itemize}
@@
 The technology consists of many different moving parts.
-In particular, OpenStack has nine key components that can be identified as part of the ”core”.
+In particular, OpenStack has nine key components that can be identified as part of the 'core'.
 Officially, OpenStack community maintained these system.
@@
 
-OpenStack is is of an open nature, anyone can add additional components to OpenStack to help it to meet their needs.
+OpenStack is is of an open nature, anyone can add additional components to OpenStack to help it  meet their needs.
 Because of the high scope of OpenStack we have at our disposal several bugs that we are interested in.
@@
 Also acts directly upon storage, providing hardware or software.
-    \item Cinder Schedule: Selects the node to storage and volume where created.
+    \item Cinder Scheduler: Selects the node to storage and volume where created.
 \end{itemize}
@@
 
-Analyzing Cinder repository we would like obtain a percentage of how many errors have been inserted by the previous commit.
-Owing to the fact that the actual premise assumes that the error was introduced by previos commit.
+In analyzing Cinder repository we would like obtain a percentage of how many errors have been inserted by the previous commit owing to the fact that the actual premise assumes that the error was introduced by previous commit.
 It is important to be able to demonstrate that existing others factors contribute to the appearance of these errors.
@@
 We need to be able to analyze a set of true tickets which will help us to reach the desired conclusion.
-Firstly, we have chosen a repository from Cinder, where we can find a wide group of tickets.
-These tickets have a state of progress, it is an updating of its status from opening the ticket until closing.
-We only are interested in closed ticket and its releas patch,  that is, whose status is “Fix released” or “Fix Commited”.
+Firstly, we have chosen a repository from Cinder, where we can find a wide group of tickets.These tickets have a state of progress, it is an updating of its status from opening the ticket until closing.
+We only are interested in a closed ticket and its release patch,  that is, whose status is 'Fix released' or 'Fix Committed'.
+
 Before reaching the goal, we have to answer intermediate questions which provide us with information throughout the analysis. 
@@
 
+\subsection{First Stage}
 \item Where will we find a ticket?
 
-The ticket are found in \url{https://bugs.launchpad.net/cinder}, where we must do an advanced search with a main search parameter called ”status" as:
+The ticket are found in \url{https://bugs.launchpad.net/cinder}, where we must do an advanced search with a main search parameter called 'status' as:
 \begin{itemize}
@@
 
-Once determined, we choose a ticket, we must to read carefully the title and the description of the ticket as well as the title of the commit which fixed the patch, because this is where will obtain more information from.
+Once determined, we choose a ticket, we must to read carefully the title and the description of the ticket as well as the title of the commit which fixed the patch, because this is where will obtain more information.
 
 The title and the description of the ticket whose id is 'n\_ticket' can be found in \url{https://bugs.launchpad.net/cinder/+bug/n_ticket}.
-The title of the commit can, sometimes be found in the same link under the comment “Fix merged to cinder (master)”, where we can find link leads to the review of the ticket \url{https://review.openstack.org/#/c/n_review}.
+The title of the commit can, sometimes be found in the same link under the comment 'Fix merged to cinder (master)', where we can find link leads to the review of the ticket \url{https://review.openstack.org/#/c/n_review}.
 In the review all the information about the patch that fixed the bug is shown.
@@
 
-In the experiment, we only have focused in the ‘It is an error’ group, as this is the ticket group that interests us.
+In the experiment, we only have focused in the 'It is an error' group, as this is the ticket group that interests us.
 
@@
 Sometimes, after having read the description of the ticket, we know if the ticket is an upgrade error.
-In this case, the answer to the question Is there a bug responsible?
-is negative.
+In this case, the answer to the question 'Is there a bug responsible?' is negative.
 That is, according to our criteria nobody is responsible for the evolution of the code.
@@
 \item What kind of code is it?
+We assume there are three kinds of codes depending on the character of the lines, which are on the involved files.
+\begin{enumerate}
+    \item New Code: When every change is executed, lines were added to each of the files.
+    \item Deleted Code: When every change was  executed, there were deleted lines in each of the files.
+    \item Modified Code: When the previous two codes are combined. This is the most common type of code (Write a percentage).
+
+\end{enumerate}
+
+Being able to classify the involved code helps us to obtain a first prediction regarding the difficulty in finding the responsible commit.
+According to our experience analyzing these 100 tickets,  the modified code and the deleted code are better than the new code because we have a limited reference as to  where the application was failing.
+
+(The following questions arise;
+Should I write about the problems of analyzing the modified code? 
+For example: the order of the functions can be changed between the previous commit and the actual commit, when in fact, there is no change.
+Should I write about the problems of analyzing a new code? 
+For example: Is the new code added, part of a previous function or is it only a new feature?)
 
 \item What number of commits are involved?
+ Using 'git blame' command in our local cinder repository, we are told what revision and author last modified each line of a file.
+We only focus on the involved lines of each implicated file, so after executing this command we get a list with all the previous commits, which could be the responsible for the bug.
+
+At times, we can discard some commits belonging to the previous list due to the commit only adding a blank line, added or modified commentaries, or maybe, it adds to the actual number of the version file.
 
 \item What will happen if the number of folders is greater than one? 
+Ideally a bug is involved in a single file.
+But unfortunately it is not always true, therefore, for these cases we will analyze all files globally as if they were one.
+So, we could have more than one responsible commit of the bug.
+
+We must pay attention when several consecutive lines were modified in a file, it can happen that they were cut and pasted.
+Even during the previous commits, this would have been happening and therefore the previous commit was not directly responsible for the error.
+If not that, it could have come from a previous commit and because of cutting and pasting it has been transferred from to commit to commit.
 
 \item Is it only the previous commit that is involved?
+In most cases, if we find a commit that acts along the same lines that have fixed the error, it is a responsible commit.
+Although there are exceptions, for example, we can find 'forks' commits, i.e.
+a code that was copied from another repository.
+These new files will have the same initial commit which is not responsible for the previous errors.
+
+We must keep in mind the initial description, because it has usually explained what is happening and together with the code and the commit of the patch, we can understand how it has been solved.
+On occasion, as when a feature is required,  we may conclude that the commit involved is not responsible for the error.
+The code evolves, so although we find commits involved in these lines, we must review the description should a case like this occur.
+
+\subsection{Second Stage}
+it is now that we continue with the next stage, where we can obtain a percentage of how many bugs have been introduced by a commit.
+To understand the second stage, we will explain some fields, important to us, which have been extracted from a review of the ticket.
+There could be more, but these are the most representative for us:
+
+We use the 'git diff commit1 commit2' command to calculate the next parameters:
+\begin{enumerate}
+    \item Number of added lines: Are the number of lines in a file ,which have been added in the actual commit (commit2) with respect to the previous commit (commit1).
+    \item Number of deleted lines:   Are the number of lines in a file, which have been deleted in the actual commit with respect to the previous commit.
+    \item Number of modified lines:  Are the sum between the number of added lines and the number of deleted lines. 
+\end{enumerate}
+
+We use the 'git blame file' command to calculate, manually at the moment.
+\begin{enumerate}
+    \item Number of previous commits: The total number of commits appearing in the lines involved.
+    \item Is each of the identifiers of each of the above commits involved in the bug.
+\end{enumerate}
+
+Now, with all the information that we have extracted, we are be able to answer the last question and our objetive for that investigation.
 
 \item Is this the commit responsible?
+In the same file we can find several commits involved, but not everyone has to be responsible for the commit.
+Therefore, comparing the status of the file, before commit and after commit, we are be able to identify those commits that are responsible and those that are not.
+Therefore, we know the degree of involvement of each of the commits involved if we classify them according to their responsibility in:
+
+\begin{enumerate}
+    \item It is responsible for the bug   
+     \item It is not responsible for the bug
+    \item Unknown responsible for the bug
+\end{enumerate}
+
+Finally, we can start with the analysis of the result obtained in this experiment.
+
 \end{itemize}
@@
 \section{The results}
+\subsection {Keywords}
 
+\subsection {Percentage of the first classification}
+\subsection {Percentage of the fsecond classification}
+
+\section{Automation}
 \section{Conclusions}

### 2015-07-14 Bug_Insertion.tex
Modifying paper

--- 2015-04-07 Bug_Insertion.tex
@@
 \usepackage{geometry}
+\usepackage{graphicx}
+\graphicspath{ {images/} }
 
@@
 \begin{abstract}
-The objective of this paper is to prove that the bug can be not caused by the previous commit.
-Currently, the premise establishes that all the bugs were introduced by the previous commit.
-We have carried out an experiment which has helped us show results pointing out a minor disagreement with the present premise.
-We have observed three stages totally separable throughout the execution of this experiment.
-The first stage considers a classification, based on our knowledge of the ticket, in three groups:
- 1.It is an error. 
- 2.It is not an error. 
- 3.Unknown. 
- The second stage involves the analysis of it as an error.
-In this stage where, with some parameters of interest, we are able to give a percentage of how many prior commits were responsible for the bug.
-The third stage is the implementation of an analytic tool to help us with the first and second stages. 
-In this paper we focus in two first stages. Explaining clearly and concisely the methodology used in our experiment.
+This is a study about code review, the main objective in this paper is the study of when an error was caused by the previous commit, where a commit is a change to the source code submitted.
+For us, the previous commit is the commit immediately prior.
+[Literature about how a bug is introduced (the fixed bugs are introduced by the previous commits)].
+However, there is not enough empirical evidence.
+We have conducted an observational study that englobes one hundred tickets extract from a free and open-source cloud computing software platform.
+The experiment was focused as a first approach to prove the premise established does not hold for all cases.
+The results of this study shows a trend in the data involving that non fixed bugs were introduced by the prior commit.
 
@@
 
+\section{Introduction}
+
+From the initial studies an implicit assumption was mentioned in which errors were caused by the previous commit as in [Kim et al., 2008] Kim, S., E.
+James Whitehead, J., and Zhang, Y.
+(2008).
+Classifying software changes: Clean or buggy?
+IEEE Transactions on Software Engineering.
+Where the authors introduce a new technique to classify changes into two main categories, buggy or clean.
+But they take on that the last commit in the line was where the responsible bug was.
+[Write more references]
+
+[ Find an autor who has doubts about this ....] .
+Nevertheless, we doubt that this empirical evidence exists and decided to try in a particular case of OpenStack.
+OpenStack is an open source cloud computing platform for all types of clouds, this project was created by developers and cloud computing technologists from around the world.
+OpenStack is a good project to be analyzed because of their high scope and their heterogeneous nature, hundreds developers are contributing to provide an infrastructure for the world's largest brands.
+OpenStack has merged around 609 reviews and about 310 tickets were closed in the last week.
+Statistics have been provided by Bicho, a tool which retrieves and organizes information from issue tracking systems.
+Specifically, 69 tickets were closed in Cinder, the repository that we are analyzing, last month June.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=1\textwidth]{cinder}
+\caption{Evolution over the years of tickets closed and closers   } \label{fig:cinder}
+\end{figure}
+
+The study is based on an empirical experiment where one hundred tickets were extracted from an specific repository of OpenStack.
+Understanding the ticket as a written evolution of a bug from it is opening until it is fixed, aka bug report.
+The analysis of these tickets helps us to scope the principal aim, which it is none other than find the cases where we can corroborate that the error was caused by the previous commit.
+
+The present study answers the following research questions:
+\begin{itemize}
+	\item Research question 1 : Is the ticket analyzed a real bug? 
+	\item Research question 2: What percentage of real bug fixes can we corroborate, in a safe way, that the antecesor change caused the error? 
+	\item Research question 3: What percentage of real bug fixes can we corroborate, in a safe way, that the antecesor change did not cause the error? 
+	\item Research question 4: How can we classify the antecesor changes? 
+\end{itemize}
+
+This paper describes our empirical experience to classify the percentage times that the actual
+teorema is correct, is not correct and is difficult to give a proper classification.
+We discuss how to extract data from a specific repository and classify them as well as how the experiment was done in Section 2.
+The research questions are answered in section 2.1 y 2.2.
+Section 3 explains some of the threats that our experiment is exposed to, the intrinsic characteristics and the extrinsic characteristics.
+Section 4 closes with the conclusions of this study.
+?
 \section{The experiment}
 
-Our experiment consisted of the analysis of one hundred tickets which were taken randomly from Cinder repository.
-We will call the first stage ‘the filtering’ as we will classify them into three categories:
+We have carried out an empirical experiment where one hundred tickets were analyzed.
+These tickets were taken randomly from Cinder repository.
+Cinder is a component of OpenStack, it works as a Block Storage manipulating volumes and snapshots.
+Cinder has a Data Base in which the state of each volume can be found.
 
-\begin{enumerate}
-    \item It is an error.
-    \item It is not an error.
-    \item Unknown
-\end{enumerate}
-
-Two different people with knowledge about programming were responsible for classifying these tickets in accordance with their opinion of the three categories mentioned above.
-The two people worked in parallel during the filtering.
-Only when all the tickets were classified were both classifications compared.
-Those whose classification were different, were compared with each other, thus reaching an agreed classification.
-After filtering, we continued to the next stage, in which we only kept in mind those tickets belonging to ’It is an error’ group.
-In this phase we were able to conclude whether the bug was added in an earlier commit, or by contrast, if it was not.
-This stage is still being validated on account of a shortage of tickets analyzed.
-At this moment, we can design an efficient algorithm that involves relevant parameters to reach the conclusion that we are looking for.
-So, for the moment, we are using these parameters as a support.
-
-\section{Several questions we have to answer}
-
-To provide a context, we have to answer some questions referring to the project from which we have taken the information. Likewise, we are going to describe the specific vocabulary.
-\begin{itemize}
-\item What is OpenStack?
-
-It is a combination of software tools for building and managing cloud computing platforms for public and private clouds.
+OpenStack is a combination of software tools for building and managing cloud computing platforms for public and private clouds.
 Principally, users deploy it as an infrastructure as a service (IaaS) solution.
 The technology consists of many different moving parts.
-In particular, OpenStack has nine key components that can be identified as part of the ”core”.
+In particular, OpenStack has nine key components that can be identified as part of the 'core'.
 Officially, OpenStack community maintained these system.
@@
     \item Networking (Neutron) provides the networking capability for OpenStack managing IP addresses.
-    \item Dashboard (Horizon) is the only graphical interface to OpenStack whereby administrators gain graphical access.
+    \item Dashboard (Horizon) is the only graphical interface to OpenStack whereby administrators can gain graphical access.
     \item Identity (Keystone) provides a central directory of users mapped to the OpenStack services that administrators and users can access.
@@
 
-\item How can OpenStack help us?
-
-OpenStack is is of an open nature, anyone can add additional components to OpenStack to help it to meet their needs.
-Because of the high scope of OpenStack we have at our disposal several bugs that we are interested in.
-The first of which is in Cinder.
-
-\item What is Cinder in OpenStack?
-
-Cinder is a component of OpenStack, it works as a Block Storage manipulating volumes and snapshots. Cinder has a Data Base in which the state of each volume can be found.
-At the same time, Cinder is composed of:
-
+We focused in Cinder repository, which is composed of:
 \begin{itemize}
@@
 Also acts directly upon storage, providing hardware or software.
-    \item Cinder Schedule: Selects the node to storage and volume where created.
+    \item Cinder Scheduler: Selects the node to storage and volume where created.
 \end{itemize}
 
-\item What would we like to achieve by analyzing this repository?
+The experiment consists of two stages in which two different persons with knowledge of programming working in parallel analyzed and classified the tickets.
+Only at the end of the two stages did these people compare the results with each other, thus reaching an agreed classification when a problematic difference was found.
+?
+\subsection{First Stage}
+The first stage considers a classification, based on our knowledge about the ticket we have analyzed, in three groups: 1.
+When we are sure that the ticket it is an error.
+2.When we are sure that the ticket it is not an error.
+3.When we have doubts about how classify the ticket, it is hardly classifiable.
+Henceforth, we will refer to group 1 as 'Error', group 2 as 'Not Error' and group 3 as 'Undecided'.
+In OpenStack, bugs reports for a project are generally tracked on Launchpad of this project, so in our case, we extracted the bugs reports from Launchpad Cinder at https://bugs.launchpad.net/cinder.
+Bugs reports with different status' are being found at this Launchpad, but we only are interested in tickets whose states are 'Fix Committed' or 'Fix Released' because only in these cases the changes in the code are visible.
+Each ticket has an id unique at Launchpad, and with this id we can see all the information about the bug.
 
-Analyzing Cinder repository we would like obtain a percentage of how many errors have been inserted by the previous commit.
-Owing to the fact that the actual premise assumes that the error was introduced by previos commit.
-It is important to be able to demonstrate that existing others factors contribute to the appearance of these errors.
-
-\item What do we have to analyze in this repository
-
-We need to be able to analyze a set of true tickets which will help us to reach the desired conclusion.
-Firstly, we have chosen a repository from Cinder, where we can find a wide group of tickets.
-These tickets have a state of progress, it is an updating of its status from opening the ticket until closing.
-We only are interested in closed ticket and its releas patch,  that is, whose status is “Fix released” or “Fix Commited”.
-Before reaching the goal, we have to answer intermediate questions which provide us with information throughout the analysis. 
-First of all, we must be clear in what we will analyze and where we can find the necessary data for this analysis. So, the first questions are:
-
-\item What is a ticket?
-
-We call a ticket each of the entries that are published in \url{https://bugs.launchpad.net/cinder}, describing a bug.
-The purpose is to leave a written a evolution of the bug from its opening until it is fixed.
-
-\item Where will we find a ticket?
-
-The ticket are found in \url{https://bugs.launchpad.net/cinder}, where we must do an advanced search with a main search parameter called ”status" as:
-\begin{itemize}
-    \item Fix Committed: the changes are pending, and to be uploaded soon.
-    \item Fix Released: a fix was uploaded to an official Cinder repository.
-\end{itemize}
-
-The next stage is to choose a random ticket and analyze it.
-Trying to answer the following questions until arriving at our objective.
-To answer the main questions, from the first level; we need to ask questions at the second level.
-The main questions are:
-\begin{itemize}
-    \item Is it a Bug?
-    \item Can we identify the commit responsible for the bug?
-    \item Is the previous commit responsible?
-\end{itemize}
-
-As we have mentioned before, to answer the main questions we need to answer other questions like the following:
-
-\item What do the title, the description and the commits of a ticket represent?
-
-Once determined, we choose a ticket, we must to read carefully the title and the description of the ticket as well as the title of the commit which fixed the patch, because this is where will obtain more information from.
-
-The title and the description of the ticket whose id is 'n\_ticket' can be found in \url{https://bugs.launchpad.net/cinder/+bug/n_ticket}.
-The title of the commit can, sometimes be found in the same link under the comment “Fix merged to cinder (master)”, where we can find link leads to the review of the ticket \url{https://review.openstack.org/#/c/n_review}.
-In the review all the information about the patch that fixed the bug is shown.
-
-After analyzing these three fields,  we should note the keywords of each of them, because in our opinion, they will help us in the future to develop an algorithm.
-Understanding keywords as those words that show the same pattern or are specific will help us with the classification.
-In addition, very often (We must calculate the percentage from the experiment), the description helps us to answer the question: Is it a bug?.
-
-At this stage, we are almost ready to answer the first question, Is it a bug?, Before that, we must be clear about the criteria that we will use.
-
-\item What criteria will be used?
+First of all, we must be clear in what we will analyze from the ticket that will help us to classify them.
+We must carefully read the title and the description of the ticket as well as the title of the commit which fixed the patch, because this is where we will obtain important information to decide to which group it belongs.
+Each ticket has an id unique at Launchpad, we will refer to it as 'n\_ticket', and with this id we can see all information about the bug at  \url{https://bugs.launchpad.net/cinder/+bug/n_ticket}.
+The title of the commit can, sometimes be found in the same link under the comment 'Fix merged to cinder (master)'.
+OpenStack provide us a Web interface for the Gerrit Code Review system to see proposed changes, and review them at \url{https://review.openstack.org/ }, specifically we will find this code review to each 'n\_ticket' at \url{https://review.openstack.org/#/c/n_review}, where 'n\_review' is the review unique id of each 'n\_ticket'.
+In the review code all the information about the patch that fixed the bug is shown.
 
@@
 With a test file the working order of the program is checked, in a way to give consistency to the program.
-A bug in the code, implicates there being a bug in the test file, provided that the test are implemented.
+A bug in the code, implicates there being a bug in the test file, provided that the test has been implemented.
 So, we are not interested in these files.
     \item Does the title of the ticket describe a new feature?
-It is not an error. New features are not considered errors, because there is no failure. The optimization, deletion of a dead code or new characteristics to users are involved here.
+It is not an error.
+New features are not considered errors, because there is no failure.
+The optimization, deletion of a dead code or new characteristics to users are involved here.
     \item Does the title of the ticket describe the program as not working as expected?
@@
     \item Does the title of the ticket describe that updates are required?
-It is an error.  We consider all tickets that require updating as errors, because if it is not updating  cinder is not operating as expected and will cause errors.
+It is an error.
+We consider all tickets that require updating as errors, because if it is not updating Cinder is not operating as expected and will cause errors.
 \end{itemize}
 
-Sometimes we are unable to answer all the questions due to having insufficient data or because of the complexity of the issue.
+Sometimes we are unable to answer all the questions due to having insufficient data or because of the complexity of the issue, in this case, the ticket will be classified into the 'Undecided' group.
 
-At this time, we should be able to classify the tickets according to their nature as:
-\begin{enumerate}
-    \item It is an error.
-    \item It is not an error.
-    \item Unknown
-\end{enumerate}
+At this moment, we are ready to answer the request 1 showing a graph where a percentage of the tickets are in each of three groups mentioned before showing.
 
-In the experiment, we only have focused in the ‘It is an error’ group, as this is the ticket group that interests us.
+\begin{figure}[htb]
+\centering
+\includegraphics[width=1\textwidth]{firstStage}
+\caption{Percentage of each group depending on the importance} \label{fig:firstStage}
+\end{figure}
+
+In figure ~\ref{fig:firstStage} is shown a classification of three groups which depend on the importance of label that the developers into Cinder had given to ticket.
+
+\subsection{Second Stage}
+
+In the second stage, we only focused in the analysis of 'Error' group.
+Therefore, we are committing an error in the final results due to some errors being lost when we discard the 'Undecided' group because probably in this group there are some bugs that we haven't  classified as such.
+In fact, this is not very important because the percentage of that group is only 16\% and the final results won't have relevant changes if we considered them.
+So, we decided to assume that error.
 
@@
 
-As before, to answer these questions we need to answer some questions from lower levels:
-
 Sometimes, after having read the description of the ticket, we know if the ticket is an upgrade error.
-In this case, the answer to the question Is there a bug responsible?
-is negative.
-That is, according to our criteria nobody is responsible for the evolution of the code.
+In this case, according to our criteria nobody is responsible for the evolution of the code.
 Therefore, if an update is necessary, despite being an error there is no commit responsible for the bug.
-
 In other cases, after the description we can conclude that we are unable to identify a responsible commit, because the ticket includes more than one component within OpenStack and although it has been opened in Cinder could have been closed in another repository that belongs to another component of OpenStack.
@@
 
-If the ticket is not in any of the above situations, we must be able to answer the next questions by analyzing the code of the files.
-These codes can be found in the review page of each ticket.
-If you click on the file involved,  a comparison between the status of the file before commit and the status of the file after the commit appears.
+If the ticket is not in any of the above situations, we have to analyze some characteristics of the commit as the kind of code it is, the number of commits involved and the number of folders modified by the fix commit.
+There is a free and open source distributed version control system called Git that provides us with several helpful commands for the analysis in the code review.
 
-\item What kind of code is it?
+Firstly we have cloned locally the Cinder repository using the 'git clone'.
+Then once we have chosen a ticket, extract the id of the fix commit and the id of parent commit from a web of Gerrit as well as the name of the files involved.
+We use 'git checkout id commit' to change between different status of these files, beginning with the id of the fix commit to obtain all characteristics mentioned before.
+So, using 'git blame file' command in our local repository, we find what revision and author last modified each line of a file, we save the output in a file.
+Then, we changed branch into the parent commit and did the same to later compare both files.
 
-\item What number of commits are involved?
+Continuing with the methodology of the experiment, we have assumed there are three kinds of codes depending on the character of the lines, which are on the involved files.
 
-\item What will happen if the number of folders is greater than one?
+\begin{enumerate}
+    \item New Code: When every change was executed, lines were added to each of the files.
+    \item Deleted Code: When every change was  executed, there were deleted lines in each of the files.
+    \item Modified Code: When the previous two codes are combined. This is the most common type of code as we can see in figure~\ref{fig:kindOfcode}
+\end{enumerate}
 
-\item Is it only the previous commit that is involved?
+\begin{figure}[htb]
+\centering
+\includegraphics[width=1\textwidth]{kindOfcode}
+\caption{Number of folders in each group depend on type of code} \label{fig:kindOfcode}
+\end{figure}
 
-\item Is this the commit responsible?
+Furthermore, we can obtain the number of lines which have been added or deleted. See in figure\ref{fig:linesOfcode}
+
+\begin{enumerate}
+    \item Number of added lines: Are the number of lines in a file ,which have been added in the actual commit (commit2) with respect to the previous commit (commit1).   
+     \item Number of deleted lines: Are the number of lines in a file, which have been deleted in the actual commit with respect to the previous commit.
+     \item Number of modified lines: Are the sum of the number of added lines and the number of deleted lines.
+\end{enumerate}
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=1\textwidth]{linesOfcode}
+\caption{Responsibility of each commit depend on nature of lines} \label{fig:linesOfcode}
+\end{figure}
+
+According to our experience analyzing these 100 tickets, the modified code and the deleted code are better than the new code because we have a limited reference as to where the application was failing.
+But, identifying the modified code is really difficult because the same lines could be in both files but located differently.
+So, we have been careful with this, and have checked it manually.
+We use 'diff -B file1 file2' command to display line\-by\-line difference between two files, the option \'-B' meaning ignore blank lines.
+Diff is an algorithm extensively explained at [Ukkonen, 1985, Miller and Myers, 1985, Myers, 1986]  which provides us several source code management systems.
+This tool examines both files and returns  what changes, showing the number of line, need to be made for first file and second file to match, that is, returns the differences found between them.
+
+At this stage, we got a list with all the previous commits, which could be the responsible  for the bug.
+At times, we can discard some commits belonging to the previous list due to the commit only adding a blank line, added or modified commentaries, or maybe, it adds to the actual number of the version file.
+
+Once we have that list, we have to identify those commits responsible.
+When there are more than one commit implicated in the same file, not everyone has to be responsible for the commit.
+Therefore, comparing the status of the file, before commit and after commit, we are be able to identify those commits that are responsible and those that are not.
+Obtaining the percentage of the degree of involvement of each of the commits involved  classifying them according to their responsibility in:
+
+\begin{enumerate}
+    \item It is the responsible
+     \item It is not the responsible 
+    \item Undecided
+\end{enumerate}
+
+It is now that we are ready to answer the request 2 and request 3 showing a percentage about when the antecesor change caused the error, when the antecesor change did not cause the error, and the cases hardly classifiable.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[width=1\textwidth]{secondStage}
+\caption{Responsibility depends on number of commits implicated} \label{fig:secondStage}
+\end{figure}
+
+The figure~\ref{fig:secondStage} shows the percentage of each group depending on how many commits have been implicated in the ticket.
+'More than one commits' is referring to the number of independent commits without considering tickets.
+
+[I have another graph where the responsibility in 'More than one commit' depend on the degree of responsibility of each commit inside a ticket
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.5\textwidth]{prueba}
+\end{figure}
+]
+
+\section{Threats to validity}
+
+We have analyzed only 100 tickets, so our conclusions in the main are mere estimates, but along the right line.
+This is the first big threat.
+It may happen, that only with 100 seemingly random tickets, there may be a tendency, a prior unknown which matches the day of the week or month of the year.
+
+Even so, setting aside the number of ticket analyzed, our model has a number of threats both intrinsic and extrinsic that make our model not 100\% valid.
+Begin with the intrinsic threats:Begin with the intrinsic threats:
+
+\begin{itemize}
+	\item Have not taken into account errors that have been classified into 'Undecided' group.
+	\item There could be some lax criteria involving the subjective opinion of the reviewers. 
+	\item Errors that have not been classified due to lacking of a review closed into Cinder repository.
 \end{itemize}
 
-\section{The results}
+Following with the extrinsic threats:
+	Related to developers:
+\begin{itemize}
+	\item Continually mentioned bug word into description and commit of a ticket when it is not an error. It could lead the reviewer to an incorrect classification
+	\item The lack of detail in the description of the ticket implies that reviewers should be experts in OpenStack. Increasing the percentage of group 'Undecided' if it does not. 
+	\item The personal opinion of the developers to attach a grade of importance label could modify the figure ~\ref{fig:firstStage}.
+\end{itemize}
 

### 2015-07-14 Bug_Insertion.tex
Modifying figures

@@
 
-[I have another graph where the responsibility in 'More than one commit' depend on the degree of responsibility of each commit inside a ticket
+[Another graph  figure~\ref{fig:degree}  shows the responsibility in 'More than one commit' depend on the degree of responsibility of each commit inside a ticket
 \begin{figure}[htb]
@@
 \includegraphics[width=0.5\textwidth]{prueba} 
+\caption{Degree of responsibility in more than one commit} \label{fig:degree}
 \end{figure}

### 2015-12-18 OSS_2016/latexFormat.tex
Ading files to OSS_2016

%%%%%%%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% sample root file for your contribution to an IFIP volume
% published at Springer
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%%%%%%%%%% Springer-Verlag %%%%%%%%%%%%%%%%%%%%%%%%%%

% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[ifip]{svmult}

% choose options for [] as required from the list
% in the Reference Guide, Sect. 2.2
\usepackage{url}
\usepackage{epsfig} 
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage{float}           % H para posicionar figuras
\usepackage{booktabs}
% etc.
% see the list of further useful packages
% in the Reference Guide, Sects. 2.3, 3.1-3.3

\makeindex             % used for the subject index
                       % please use the style sprmidx.sty with
                       % your makeindex program

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title*{Contribution Title}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Gema Rodriguez\inst{1}}
%\and Name of Author\inst{2}}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
 \institute{}
%\texttt{name@email.address}
%\and Name and Address of your Institute \texttt{name@email.address}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle
\section{Introduction} 
\label{sec:1}

Many efforts on how and why bugs are introduced in the software source code are underway in the software engineering research community. Software source code is affected by many changes, many of them due to failure of the software because of emergent bugs.

While a software system is being developed, software engineers use version repository to produce and manage their code. Developers and tester reported issues, which are stored in other repository known as issue-tracking system, when a wrong behavior or bugs are found in the systems.

Issue-tracking systems help solving these bugs, but their problem is the difficulty of distinguish the bug reports from other are not. These systems provide an interface to manage reports of maintenance activities. The developers report issues describing bug reports, features or optimizations. During the bug-seeding process is difficult distinguish bug reports from other issues due to the misclasification, a study describes that two of five issues was misclassified \cite{Herzig}. The misclassified causes bias predecting bugs whether non bug reports are taken into account.

To classify issues as bug reports or non bug reports we could use automatic classification system as is described in\cite{Antoniol}, but the vocabulary used in the issues could change as well as the policy depending on the project. Consequently, data validation is recomended in the studies\cite{Herzig}.

Recording links between bug reports in a issue-tracking system and the corresponding fix-commit is a hard work, causing a lost time looking in issue-tracking systems and version repositories.

Traditionally, the methods used in link recovery \cite{Zimmermann, Thomas} are based on text patterns or the mining of key phrases. Unfortunately, this methods include several false negatives causing bias in data \cite{Bird, NguyenTH}. Therefore other methods could to be developed such as Mlink approach that links bug report with fixes using feauters in the changed source files corresponding to commit logs in addition to the traditional textual features \cite{Nguyen}. But all of them suppose that the issues are bug report. Hence, we propose a tool to display the data necessary to the developers/testers, who could decide whether the issue is a bug report or not. The developers know better than other the system,therefore the tool help their to choose only bug reports to be analyze in bug-seeding process removing any bias induced by non bug reports.

\section{The tool} 
\label{sec:2}
The tool works in the browser, displaying the main characteristics to distingush bug report from others in OpenStack project, the developers will be responsibles to classify the tickets as bug report or not, could explain his decisions in each ticket.

OpenStack was particularly of interest because of its highest scope and heterogeneous nature with hundreds of developers contributing, futhermore due to its short life, only 5 years, all history is saved and available in a version control system. The issues are called tickets in OpenStack and availables in the Launchpad, a web interface of ticket tracking system, classifying them as bug report or not.

\subsection{Architecture}
This project works with Launchpad as issue-tracking system and Gerrit as code review system. The image \ref{fig:1} presents the architecture used in the tool, which has been developed with JavaScript, Node, JQuery and HTML5 technologies. The server side works making queries to the API of Gerrit an Launchpad, and the client side is where the user can see the information displayed. The client side interacts with the server through events. Both sides share the information requiered using JSON files. Futhermore, to integrate some funtionatities from github, we use a third-party application between github and the browser.

\label{sec:2.1}
\begin{figure}
\centering
\includegraphics[height=4cm]{Arquitectura.png}
\caption{Architecture}
\label{fig:1}       % Give a unique label
\end{figure}

\subsection{Main Features}
\label{sec:2.2}
The tool shows the id of the tickets, which are extracted randomly from each issue-tracking repository of OpenStack, and displays the information necessary to decide whether the issue is a bug report or not. We focused in display the main parameters that help in the classification, such as the title of the report and the description as well as the description of the fix commit.

The left side in the image \ref{fig:2}, shows the information related with the ticket in Launchpad and its correspondent fix-commit in Gerrit. Some information displayed link with the original pages in Launchpad and Gerrit, thereby the  developers have at their disposal extra information such as the comments that other developers have done. Could tracking the history since the ticket opens until the commit fixed the ticket.

The right side is guided to user's opinion, after reading all the information displayed, they have to classify the ticket as \textit{Bug report} or \textit{Not Bug report}. Due to unsophisticated description used in the ticket, the developers could doubt in the classification, for this reason we add an extra option in the classification, \textit{Undecided}. Futhermore, the developers have a textarea to write their opinion about their classification in each ticket, as well as other textareas to write the keywords found in the title and the description which can help us building an automatic classification system in the future.

The tool allow carry out a double bind analisys, due to the data is saved in github user's account. In order that, the user can only see and modify their own data saved. Github is a control version system in which we have access to the whole information of each commit submitted by the developer. Thus, saving the data in Github, we could measure the time that each developer spend in the analisys, which tickets were more difficult to anaylize and other statistics that can help us undertanding the current problem of issues misclassification.

We continue developing the tool but an initial version is available \footnote{\url{bugtracking.libresoft.es}}, as well as a demonstration video\footnote{\url{https://www.youtube.com/watch?v=q0-TIvL4mqc&feature=youtu.be}}. It presents a licence type GPL 0 (General Public License) and you can find the code in my github's account\footnote{\url{https://github.com/Gemarodri/BugTracking}}. Anyone can use it regardless of have github account or not. But, they only can save and modify their data, in addition, one of the requirements to save and modify data is create a new repository with the same name that the repository of OpenStack you want to analyze.

\begin{figure}
\centering
\includegraphics[height=10cm]{index.png}
\caption{Screenshot of Index}
\label{fig:2}       % Give a unique label
\end{figure}
\section{Validation Study} 
\label{sec:3}

We use the tool to analyze randomly 500 tickets, reported in the last year, from the four principal repositories in OpenStack. This tickets could be tagged as either "Fix Commited" or "Fix Released", to be able to localizate the patch implemented into de source code in the version repository. They are generally tracked in Launchpad \texttt{Nova},\texttt{Cinder},\texttt{Horizon} and \texttt{Neutron}\footnote{\url{https://bugs.launchpad.net/NameOfRepository}}

The parameters analyzed for each ticket were the title and the description of the report and the description of the fix commit. Also, the code changes if neither the descriptions and the comments clarified the underlying tiket. Each ticket was then categorized into one of three following groups.
\begin{enumerate}
  \item The ticket describes a bug report.
  \item The ticket describes a feature, an optimitazion code, changes in test files or other not bug reports.
  \item The ticket presents a vague description and cannot be classified without doubts. 
\end{enumerate}

Henceforth, we will refer to Group 1 as \textit{Bug Report}, Gruop 2 as \textit{not Bug Report} and Group 3 as \textit{Undecided}.

In the analisys were involved three different developers who used a double bind review process, obtaining that each tickets was analyzed by two developers. Each developer analyzed 167 tickets plus the half tickets of his teammates. %Only at the end, they disscused the classification conflicts to reach an agreement.

\section{Results} 
\label{sec:4}
We have manually analyzed 500 tickets with support of the present tool. The table ~\ref{tab:1} show the statistics of each developer after analysed 334 tickets.

\begin{table}[htb]
\begin{center} {\footnotesize
\caption{ Classification statistics of each developer}
\label{tab:1}
\begin{tabular}{llll}
\toprule[0.3mm]%{\smallskip}
  & Bug Report\kern 1pc & Not Bug Report\kern 1pc & Undecided \\\hline
Developer 1 \kern 1pc & 53.89\% & 34.13\% & 11.98\% \\
Developer 2 \kern 1pc & --\% & --\% & --\% \\
Developer 3 \kern 1pc & --\% & --\% & --\% \\
\bottomrule[0.3mm]
\end{tabular} }
\end{center}
\end{table}

(should we corroborate that the statistics are similar with the previous study where only 100 tickets were analyse?\\
results with 100 tickets: (63\%) have been considered as Bug Report, (21\%) as Not Bug Report, and (16\%) as Undecided) 
)
% Developer 1: 334 tickets
% H--Ne--C--No
% 64+50+31+35 --> 180 -->(53.89%)
% 45+26+24+19 --> 114 -->(34.13\%)
% 16+7+8+9 --> 40 --> (11.98\%)

\section{Discussion}
\label{sec:5}
How to procede if there are discordances beetween the developers:

- Should the developers disscuss after their analisys to reach a better classification?
- Does the bug report only the same ticket classified as Bug report for all the developers?

\subsection{Future Work}
\label{sec:5.1}

We would like know what grade of responsability, none or totally, practice the previous commit in the seeding of a bug in OpenStack, considering that currently exists an implicit assumption: the line that contains the error was caused by the inmediately previous commit\cite{Sliwerski}. The accuracy in our results depends on the quality of the data, thus we should focus only on bug reports discarding the other issues.

- Implement this part in the tool, displaying the code after and before the bug fixed and after and before the bug-introduction to determinate if the previous commit is responsible or not.

\section{Knowleadges}
\label{sec:6}

\input{referenc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\printindex
\end{document}

### 2015-12-18 OSS_2016/referenc.tex
Ading files to OSS_2016

%%%%%%%%%%%%%%%%%%%%%%%% referenc.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% sample references
% "computer science"
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%%%%%%%%%% Springer-Verlag %%%%%%%%%%%%%%%%%%%%%%%%%%

%
% BibTeX users please use
% \bibliographystyle{}
% \bibliography{}
%
% Non-BibTeX users please use
\begin{thebibliography}{99.}
%
% and use \bibitem to create references.
%
% Use the following syntax and markup for your references
%
% Monographs
%\bibitem{monograph} Kajan E (2002)
%Information technology encyclopedia and acronyms. Springer, Berlin
%Heidelberg New York

% Contributed Works
%\bibitem{contribution} Broy M (2002) Software engineering -- From
%auxiliary to key technologies. In: Broy M, Denert E (eds)
%Software Pioneers. Springer, Berlin Heidelberg New York
\bibitem{Antoniol}Antoniol, Giuliano, et al. Is it a Bug or an Enhancement? A Text-based Approach to Classify Change Requests. 2008.
\bibitem{Herzig}Herzig, Kim; Just, Sascha; Zeller, Andreas. It's not a Bug, it's a Feature: How Misclassification Impacts Bug Prediction. month, 2012.
\bibitem{Sliwerski}J. Sliwerski, T. Zimmermann, and A. Zeller. When do
changes induce fixes? ACM sigsoft software engineering
notes, 30(4):1–5, 2005.
\bibitem {Nguyen}Nguyen, Anh Tuan, et al. 'Multi-layered approach for recovering links between bug reports and fixes.'' Proceedings of the ACM SIGSOFT 20th International Symposium on the Foundations of Software Engineering. ACM, 2012.
\bibitem {Zimmermann}Zimmermann, Thomas; Premraj, Rahul; Zeller, Andreas. Predicting defects for eclipse. En Predictor Models in Software Engineering, 2007. PROMISE'07: ICSE Workshops 2007. International Workshop on. IEEE, 2007. p. 9-9.
\bibitem{Thomas}Zimmermann, Thomas, and Peter Weißgerber. "Preprocessing CVS data for fine-grained analysis." Proceedings of the International Workshop on Mining Software Repositories. 2004.
\bibitem{Bird}Bird, C., Bachmann, A., Aune, E., Duffy, J., Bernstein, A., Filkov, V., \& Devanbu, P. (2009, August). Fair and balanced?: bias in bug-fix datasets. In Proceedings of the the 7th joint meeting of the European software engineering conference and the ACM SIGSOFT symposium on The foundations of software engineering (pp. 121-130). ACM.
\bibitem{NguyenTH}Nguyen, T. H., Adams, B., \& Hassan, A. E. (2010, October). A case study of bias in bug-fix datasets. In Reverse Engineering (WCRE), 2010 17th Working Conference on (pp. 259-268). IEEE.
% Journal
%\bibitem{journal} Che M, Grellmann W, Seidler S (1997)
%Appl Polym Sci 64:1079--1090

% Theses
%\bibitem{thesis} Ross DW (1977) Lysosomes and storage diseases. MA
%Thesis, Columbia University, New York

\end{thebibliography}

### 2015-12-30 OSS_2016/latexFormat.tex
Modifying

@@
 
-\title*{Contribution Title}
+\title*{BugTracking: A tool to assist in the Bug Triage Process}
 % Use \titlerunning{Short Title} for an abbreviated version of
 % your contribution title if the original one is too long
-\author{Gema Rodriguez\inst{1}}
+\author{Gema Rodriguez\inst{1}\and Jesus M. Gonzalez-Barahona\inst{1}}
 %\and Name of Author\inst{2}}
@@
 % your contribution title if the original one is too long
- \institute{}
-%\texttt{name@email.address}
-%\and Name and Address of your Institute \texttt{name@email.address}}
+\institute{\texttt{gerope@libresoft.es}, \texttt{jgb@gsyc.es}
+\and GSyC/LibreSoft, Universidad Rey Juan Carlos}
 %
@@
 
-While a software system is being developed, software engineers use version repository to produce and manage their code.
-Developers and tester reported issues, which are stored in other repository known as issue-tracking system, when a wrong behavior or bugs are found in the systems.
+While a software system is being developed, software engineers use version repositories to produce and manage their code.
+Developers and tester report issues, which are stored in other repositories, known as issue-tracking system, when a wrong behavior or bugs are found in the systems.
 
-Issue-tracking systems help solving these bugs, but their problem is the difficulty of distinguish the bug reports from other are not.
-These systems provide an interface to manage reports of maintenance activities.
-The developers report issues describing bug reports, features or optimizations.
-During the bug-seeding process is difficult distinguish bug reports from other issues due to the misclasification, a study describes that two of five issues was misclassified \cite{Herzig}.
-The misclassified causes bias predecting bugs whether non bug reports are taken into account.
+Issue-tracking systems help solving these bugs, but their problem is the difficulty of distinguish the bug reports from other that are not bugs.
+These systems provide an interface to manage reports of maintenance activities where developers can report issues describing bug reports, features or optimizations.
+During the bug triage process it is difficult to distinguish bug reports from other issues; a study describes that two of five issues are misclassified~\cite{Herzig}.
+This misclassification causes bias predicting bugs wher non-bug reports are taken into account.
 
-To classify issues as bug reports or non bug reports we could use automatic classification system as is described in\cite{Antoniol}, but the vocabulary used in the issues could change as well as the policy depending on the project.
-Consequently, data validation is recomended in the studies\cite{Herzig}.
+To classify issues as bug reports or non bug reports we can use automatic classification systems as the one described in~\cite{Antoniol}, but the vocabulary used in the issues could change from project to project, as well as the policy depending on the project.
+Consequently, data validation is recommended in the studies~\cite{Herzig}.
 
-Recording links between bug reports in a issue-tracking system and the corresponding fix-commit is a hard work, causing a lost time looking in issue-tracking systems and version repositories.
+Linking a bug reports in a issue-tracking system and the corresponding fix-commit may be not a trivial task.
+Traditionally, the methods used in link recovery~\cite{Zimmermann, Thomas} are based on text patterns or the mining of key phrases.
+Unfortunately, these methods can include  many false negatives causing bias in data~\cite{Bird, NguyenTH}.
+Therefore other methods, such as Mlink approach, have been developed that link bug report with fixes using features in the changed source files corresponding to commit logs in addition to the traditional textual features~\cite{Nguyen}.
+But all of them suppose that the issues are bug reports.
 
-Traditionally, the methods used in link recovery \cite{Zimmermann, Thomas} are based on text patterns or the mining of key phrases.
-Unfortunately, this methods include several false negatives causing bias in data \cite{Bird, NguyenTH}.
-Therefore other methods could to be developed such as Mlink approach that links bug report with fixes using feauters in the changed source files corresponding to commit logs in addition to the traditional textual features \cite{Nguyen}.
-But all of them suppose that the issues are bug report.
-Hence, we propose a tool to display the data necessary to the developers/testers, who could decide whether the issue is a bug report or not.
-The developers know better than other the system,therefore the tool help their to choose only bug reports to be analyze in bug-seeding process removing any bias induced by non bug reports.
+In this paper, we propose a tool to display the data necessary to the developers/testers, who could decide whether the issue is a bug report or not.
+The developers have the best available knowledge of their system, therefore the tool will help them choosing only bug reports to be analyzed in the bug-triage process removing any bias induced by non bug reports.
 
@@
 \label{sec:2}
-The tool works in the browser, displaying the main characteristics to distingush bug report from others in OpenStack project, the developers will be responsibles to classify the tickets as bug report or not, could explain his decisions in each ticket.
 
-OpenStack was particularly of interest because of its highest scope and heterogeneous nature with hundreds of developers contributing, futhermore due to its short life, only 5 years, all history is saved and available in a version control system.
-The issues are called tickets in OpenStack and availables in the Launchpad, a web interface of ticket tracking system, classifying them as bug report or not.
+The tool works in the browser, displaying the main characteristics to distinguish bug report from others.
+Developers will be responsible to classify the tickets as bug report or not, could explain his decisions in each ticket.
 
 \subsection{Architecture}
+
 This project works with Launchpad as issue-tracking system and Gerrit as code review system.
@@
 The client side interacts with the server through events.
-Both sides share the information requiered using JSON files.
-Futhermore, to integrate some funtionatities from github, we use a third-party application between github and the browser.
+Both sides share the information required using JSON files.
+Furthermore, to integrate some functionalities from GitHub, we use a third-party application between GitHub and the browser.
 
@@
 \centering
-\includegraphics[height=4cm]{Arquitectura.png}
-\caption{Architecture}
+\includegraphics[height=7cm]{Arquitectura.png}
+\caption{Architecture of the tool.}
 \label{fig:1}       % Give a unique label
@@
 Due to unsophisticated description used in the ticket, the developers could doubt in the classification, for this reason we add an extra option in the classification, \textit{Undecided}.
-Futhermore, the developers have a textarea to write their opinion about their classification in each ticket, as well as other textareas to write the keywords found in the title and the description which can help us building an automatic classification system in the future.
+Furthermore, the developers have a textarea to write their opinion about their classification in each ticket, as well as other textareas to write the keywords found in the title and the description which can help us building an automatic classification system in the future.
 
-The tool allow carry out a double bind analisys, due to the data is saved in github user's account.
+The tool allow carry out a double bind analysis, due to the data is saved in GitHub user's account.
 In order that, the user can only see and modify their own data saved.
-Github is a control version system in which we have access to the whole information of each commit submitted by the developer.
-Thus, saving the data in Github, we could measure the time that each developer spend in the analisys, which tickets were more difficult to anaylize and other statistics that can help us undertanding the current problem of issues misclassification.
+GitHub is a control version system in which we have access to the whole information of each commit submitted by the developer.
+Thus, saving the data in GitHub, we could measure the time that each developer spend in the analysis, which tickets were more difficult to analyze and other statistics that can help us understanding the current problem of issues misclassification.
 
-We continue developing the tool but an initial version is available \footnote{\url{bugtracking.libresoft.es}}, as well as a demonstration video\footnote{\url{https://www.youtube.com/watch?v=q0-TIvL4mqc&feature=youtu.be}}.
-It presents a licence type GPL 0 (General Public License) and you can find the code in my github's account\footnote{\url{https://github.com/Gemarodri/BugTracking}}.
-Anyone can use it regardless of have github account or not.
+We continue developing the tool but an initial version is available\footnote{\url{bugtracking.libresoft.es}}, as well as a demonstration video\footnote{\url{https://www.youtube.com/watch?v=q0-TIvL4mqc&feature=youtu.be}}.
+It presents a licence type GPL 0 (General Public License) and you can find the code in my GitHub account\footnote{\url{https://github.com/Gemarodri/BugTracking}}.
+Anyone can use it regardless of have GitHub account or not.
 But, they only can save and modify their data, in addition, one of the requirements to save and modify data is create a new repository with the same name that the repository of OpenStack you want to analyze.
@@
 \end{figure}
+
 \section{Validation Study} 
@@
 
-We use the tool to analyze randomly 500 tickets, reported in the last year, from the four principal repositories in OpenStack.
-This tickets could be tagged as either "Fix Commited" or "Fix Released", to be able to localizate the patch implemented into de source code in the version repository.
+OpenStack was particularly of interest because of its highest scope and heterogeneous nature with hundreds of developers contributing, furthermore due to its short life, only 5 years, all history is saved and available in a version control system.
+The issues are called tickets in OpenStack and available in the Launchpad, a web interface of ticket tracking system, classifying them as bug report or not.
+
+We use the tool to analyze randomly tickets from the four principal repositories in OpenStack.
+This tickets could be tagged as either "Fix Commited" or "Fix Released", to be able to localize the patch implemented into de source code in the version repository.
 They are generally tracked in Launchpad \texttt{Nova},\texttt{Cinder},\texttt{Horizon} and \texttt{Neutron}\footnote{\url{https://bugs.launchpad.net/NameOfRepository}}
@@
 The parameters analyzed for each ticket were the title and the description of the report and the description of the fix commit.
-Also, the code changes if neither the descriptions and the comments clarified the underlying tiket.
+Also, the code changes if neither the descriptions and the comments clarified the underlying ticket.
 Each ticket was then categorized into one of three following groups.
@@
   \item The ticket describes a bug report.
-  \item The ticket describes a feature, an optimitazion code, changes in test files or other not bug reports.
+  \item The ticket describes a feature, an optimization code, changes in test files or other not bug reports.
   \item The ticket presents a vague description and cannot be classified without doubts. 
@@
 
-Henceforth, we will refer to Group 1 as \textit{Bug Report}, Gruop 2 as \textit{not Bug Report} and Group 3 as \textit{Undecided}.
+Henceforth, we will refer to Group 1 as \textit{Bug Report}, Group 2 as \textit{not Bug Report} and Group 3 as \textit{Undecided}.
 
-In the analisys were involved three different developers who used a double bind review process, obtaining that each tickets was analyzed by two developers.
+To validate the tool four diferent developers analyzed tickets belongs to the four main repositories.
+The developers analyzed more than one hundred tickets to can probe than the tool work as them expected, clasifiying the tickets into one of the three groups and corroborating that the issues reports present misclassification as ~\cite{Herzig} mencioned.
+
+%In the analysis were involved three different developers who used a double bind review process, obtaining that each tickets was analyzed by two developers.
 Each developer analyzed 167 tickets plus the half tickets of his teammates.
@@
 \label{sec:4}
-We have manually analyzed 500 tickets with support of the present tool. The table ~\ref{tab:1} show the statistics of each developer after analysed 334 tickets.
+We have manually analyzed more than one hundred tickets with support of the present tool. The table ~\ref{tab:1} show the statistics of each developer after analyzed the tickets.
 
@@
 \label{tab:1}
-\begin{tabular}{llll}
+\begin{tabular}{lllll}
 \toprule[0.3mm]%{\smallskip}
-  & Bug Report\kern 1pc & Not Bug Report\kern 1pc & Undecided \\\hline
-Developer 1 \kern 1pc & 53.89\% & 34.13\% & 11.98\% \\
-Developer 2 \kern 1pc & --\% & --\% & --\% \\
-Developer 3 \kern 1pc & --\% & --\% & --\% \\
+  & Bug Report\kern 1pc & Not Bug Report\kern 1pc & Undecided\kern 1pc & Total \\\hline
+Developer 1 \kern 1pc & 53.89\% & 34.13\% & 11.98\% & 334 \\
+Developer 2 \kern 1pc & --\% & --\% & --\% & 125\\
+Developer 3 \kern 1pc & --\% & --\% & --\% & 125\\
+Developer 4 \kern 1pc & \% & \% & \% & 100 \\
 \bottomrule[0.3mm]
@@
 
-(should we corroborate that the statistics are similar with the previous study where only 100 tickets were analyse?\\
-results with 100 tickets: (63\%) have been considered as Bug Report, (21\%) as Not Bug Report, and (16\%) as Undecided) 
-)
+All the data is available in the github's account of the developers \footnote{\url{https://github.com/Gemarodri/Horizon}},\footnote{\url{https://github.com/ddalipaj/Cinder}}\footnote{\url{https://github.com/nellysek/Nova}}, the repositories has the same name that the projects analyzed in OpenStack.
+
+%(should we corroborate that the statistics are similar with the previous study where only 100 tickets were analyze?\\
+%results with 100 tickets: (63\%) have been considered as Bug Report, (21\%) as Not Bug Report, and (16\%) as Undecided) )
 % Developer 1: 334 tickets
@@
 \label{sec:5}
-How to procede if there are discordances beetween the developers:
 
-- Should the developers disscuss after their analisys to reach a better classification?
-- Does the bug report only the same ticket classified as Bug report for all the developers?
+Once we have all the tickets analyzed by diferents developers who have used a double blind, how to proceed if there are discordances between them:
+\begin{enumerate}
+\item Should they discuss after their analysis to reach a better classification?
+\item Does the bug report only the same ticket classified as Bug report for all the developers?
+\end{enumerate}
 
@@
 
-We would like know what grade of responsability, none or totally, practice the previous commit in the seeding of a bug in OpenStack, considering that currently exists an implicit assumption: the line that contains the error was caused by the inmediately previous commit\cite{Sliwerski}.
+We would like know what grade of responsibility, none or totally, practice the previous commit in the seeding of a bug in OpenStack, considering that currently exists an implicit assumption: the line that contains the error was caused by the immediately previous commit\cite{Sliwerski}.
 The accuracy in our results depends on the quality of the data, thus we should focus only on bug reports discarding the other issues.
 
-- Implement this part in the tool, displaying the code after and before the bug fixed and after and before the bug-introduction to determinate if the previous commit is responsible or not.
-
-\section{Knowleadges}
-\label{sec:6}
+The next step in the tool is implement the part in where we analyzed the previous commit, displaying the code after and before the bug fixed and after and before the bug-introduction to determinate if the previous commit is responsible or not.
 

### 2016-01-13 OSS_2016/paper.tex
Abstract...

--- 2015-12-30 OSS_2016/latexFormat.tex
@@
 % your contribution title if the original one is too long
-\author{Gema Rodriguez\inst{1}\and Jesus M. Gonzalez-Barahona\inst{1}}
+\author{Gema Rodriguez\inst{1}, Jesus M. Gonzalez-Barahona \and Gregorio Robles\inst{1}}
 %\and Name of Author\inst{2}}
@@
 \maketitle
+
+\begin{abstract}
+	In most software projects, but in particular in almost all free, open source software projects, issue tracking systems are used for recording many different kinds of issues: bug reports, feature requests, maintenance tickets, and even design discussions.
+Identifying which of those issues are bug reports, is not a trivial task.
+When researchers want to conduct some study on the bug reports managed by a software development project, they need to first of all to perform this identification.
+
+	The job for researchers here is very different from the bug triaging that developers do.
+In the latter case, people with a lot of experience in the project make a decission based on the information available at that time (maybe just a short comment by some user), asking if needed for more details.
+In the former case, researchers are usually not that experienced in the project, but they have at their disposal all the information produced, until the moment the issue was closed.
+This may include not only all comments and actions on the issue tracking system, but for examples, discusions about a fix in the code review system, or the final fixing patch in the source code management system.
+Having all that information conveyed to the researchers in an easy, flexible and quick way accelerates and makes much more reliable their decission making process.
+This simplifies large scale manual analysis of issues (in the hundreds or thousands), helping researchers to ensure that they are really working with what they intend to work: bug reports.
+
+	This paper presentes a tool designed exactly to solve this problem of providing the researcher with all the relevant information needed to decide if an issue corresponds to a bug report or not.
+The tool uses information extracted automatically from the project repositories, and offers a web-based interface which allows for collaboration, traceability and transparency of the identification of bug reports, making the process easier, faster, and more reliable.
+\end{abstract}
+
 \section{Introduction}

### 2016-01-14 OSS_2016/paper.tex
Adding new table

@@
 % your contribution title if the original one is too long
-\author{Gema Rodriguez\inst{1}, Jesus M. Gonzalez-Barahona \and Gregorio Robles\inst{1}}
+\author{Gema Rodriguez\inst{1}, Jesus M. Gonzalez-Barahona\inst{1} \and Gregorio Robles\inst{1}}
 %\and Name of Author\inst{2}}
@@
 % your contribution title if the original one is too long
-\institute{\texttt{gerope@libresoft.es}, \texttt{jgb@gsyc.es}
+\institute{\texttt{gerope@libresoft.es}, \texttt{jgb@gsyc.es},\texttt{grex@gsyc.es}
 \and GSyC/LibreSoft, Universidad Rey Juan Carlos}
@@
 This may include not only all comments and actions on the issue tracking system, but for examples, discusions about a fix in the code review system, or the final fixing patch in the source code management system.
-Having all that information conveyed to the researchers in an easy, flexible and quick way accelerates and makes much more reliable their decission making process.
+Having all that information conveyed to the researchers in an easy, flexible and quick way accelerates and makes much more reliable their decision making process.
 This simplifies large scale manual analysis of issues (in the hundreds or thousands), helping researchers to ensure that they are really working with what they intend to work: bug reports.
@@
 
-Many efforts on how and why bugs are introduced in the software source code are underway in the software engineering research community.
+%Many efforts on how and why bugs are introduced in the software source code are underway in the software engineering research community.
 Software source code is affected by many changes, many of them due to failure of the software because of emergent bugs.
@@
 While a software system is being developed, software engineers use version repositories to produce and manage their code.
-Developers and tester report issues, which are stored in other repositories, known as issue-tracking system, when a wrong behavior or bugs are found in the systems.
+Developers and tester report issues, which are stored in other repositories, known as issue-tracking system, where many kinds of issues can be found.
 
@@
 During the bug triage process it is difficult to distinguish bug reports from other issues; a study describes that two of five issues are misclassified~\cite{Herzig}.
-This misclassification causes bias predicting bugs wher non-bug reports are taken into account.
+This misclassification causes bias predicting bugs where non-bug reports are taken into account.
 
-To classify issues as bug reports or non bug reports we can use automatic classification systems as the one described in~\cite{Antoniol}, but the vocabulary used in the issues could change from project to project, as well as the policy depending on the project.
+To distinguish the bug reports we can use automatic classification systems as the one described in~\cite{Antoniol}, but the vocabulary used in the issues could change from project to project, as well as the policy depending on the project.
 Consequently, data validation is recommended in the studies~\cite{Herzig}.
@@
 Unfortunately, these methods can include many false negatives causing bias in data~\cite{Bird, NguyenTH}.
-Therefore other methods, such as Mlink approach, have been developed that link bug report with fixes using features in the changed source files corresponding to commit logs in addition to the traditional textual features~\cite{Nguyen}.
+Therefore other methods, such as Mlink approach, have been developed to link bug report with fixes using features in the changed source files corresponding to commit logs in addition to the traditional textual features~\cite{Nguyen}.
 But all of them suppose that the issues are bug reports.
 
-In this paper, we propose a tool to display the data necessary to the developers/testers, who could decide whether the issue is a bug report or not.
+In this paper, we present a tool to display all the data necessary to the developers to decide whether the issue is a bug report or not.
 The developers have the best available knowledge of their system, therefore the tool will help them choosing only bug reports to be analyzed in the bug-triage process removing any bias induced by non bug reports.
@@
 \centering
-\includegraphics[height=10cm]{index.png}
+\includegraphics[height=10cm]{index2.png}
 \caption{Screenshot of Index}
@@
 
-We use the tool to analyze randomly tickets from the four principal repositories in OpenStack.
+We use the tool to analyze 500 randomly tickets from the four principal repositories in OpenStack.
 This tickets could be tagged as either "Fix Commited" or "Fix Released", to be able to localize the patch implemented into de source code in the version repository.
@@
 
-To validate the tool four diferent developers analyzed tickets belongs to the four main repositories.
-The developers analyzed more than one hundred tickets to can probe than the tool work as them expected, clasifiying the tickets into one of the three groups and corroborating that the issues reports present misclassification as ~\cite{Herzig} mencioned.
+To validate the tool three different developers analyzed tickets belongs to the four main repositories.
+The developers analyzed more than three hundred tickets to can probe than the tool work as them expected, clasifiying the tickets into one of the three groups and corroborating that the issues reports present misclassification as ~\cite{Herzig} mencioned.
 
-%In the analysis were involved three different developers who used a double bind review process, obtaining that each tickets was analyzed by two developers.
-Each developer analyzed 167 tickets plus the half tickets of his teammates.
+%In the analysis, some of the tickets present a double bind review process, obtaining that each tickets was analyzed by two developers.
+%Each developer analyzed 167 tickets plus the half tickets of his teammates.
 %Only at the end, they disscused the classification conflicts to reach an agreement.
@@
 \label{sec:4}
-We have manually analyzed more than one hundred tickets with support of the present tool. The table ~\ref{tab:1} show the statistics of each developer after analyzed the tickets.
+We have manually analyzed 500 tickets with support of the present tool. The table ~\ref{tab:1} show the statistics of each developer after analyzed the tickets.
 
@@
 Developer 3 \kern 1pc & --\% & --\% & --\% & 125\\
-Developer 4 \kern 1pc & \% & \% & \% & 100 \\
 \bottomrule[0.3mm]
@@
 
-All the data is available in the github's account of the developers \footnote{\url{https://github.com/Gemarodri/Horizon}},\footnote{\url{https://github.com/ddalipaj/Cinder}}\footnote{\url{https://github.com/nellysek/Nova}}, the repositories has the same name that the projects analyzed in OpenStack.
+In the analysis, some of the tickets present a double bind review process, obtaining that each tickets was analyzed by two developers.
+The table ~\ref{tab:2} show the number of tickets analized with double bind review and the number tickets analized with only one review, as well as the percentaje of concordance obtained with the double bind.
+
+\begin{table}[htb]
+\begin{center} {\footnotesize
+\caption{ Classification statistics of each developer}
+\label{tab:2}
+\begin{tabular}{llllll}
+\toprule[0.3mm]%{\smallskip}
+  & Nova \kern 1pc & Cinder \kern 1pc & Horizon \kern 1pc & Neutron \kern 1pc & Total\\\hline
+One revision \kern 1pc & --  & -- & -- & -- & -- \\
+Double Bind  \kern 1pc & -- & -- & -- & -- & --\\
+Concordance\\
+(only in double bind) \kern 1pc & --\% & --\% & --\% & --\% & --\\
+\bottomrule[0.3mm]
+\end{tabular} }
+\end{center}
+\end{table}
+All the data is available in the repositories of github's account of the developers \footnote{\url{https://github.com/Gemarodri}}\footnote{\url{https://github.com/ddalipaj}}\footnote{\url{https://github.com/nellysek}}, these repositories has the same name that the projects analyzed in OpenStack.
 
@@
 
-\section{Discussion}
-\label{sec:5}
+%\section{Discussion}
+%\label{sec:5}
 
-Once we have all the tickets analyzed by diferents developers who have used a double blind, how to proceed if there are discordances between them:
-\begin{enumerate}
-\item Should they discuss after their analysis to reach a better classification?
-\item Does the bug report only the same ticket classified as Bug report for all the developers?
-\end{enumerate}
+%Once we have all the tickets analyzed by diferents developers who have used a double blind, how to proceed if there are discordances between them:
+%\begin{enumerate}
+%\item Should they discuss after their analysis to reach a better classification?
+%\item Does the bug report only the same ticket classified as Bug report for all the developers?
+%\end{enumerate}
 

### 2016-01-15 OSS_2016/paper.tex
Adding some data and changing the title

@@
 
-\title*{BugTracking: A tool to assist in the Bug Triage Process}
+\title*{BugTracking: A tool to assist in the identification of bug reports}
 % Use \titlerunning{Short Title} for an abbreviated version of
@@
   & Bug Report\kern 1pc & Not Bug Report\kern 1pc & Undecided\kern 1pc & Total \\\hline
-Developer 1 \kern 1pc & 53.89\% & 34.13\% & 11.98\% & 334 \\
-Developer 2 \kern 1pc & --\% & --\% & --\% & 125\\
-Developer 3 \kern 1pc & --\% & --\% & --\% & 125\\
+Developer 1 \kern 1pc & (180)-54\% & (114)-34\% & (40)-12\% & 334 \\
+Developer 2 \kern 1pc & (188)-76\% & (51)-21\% & (8)-3\% & 247\\
+Developer 3 \kern 1pc & (125)-55\% & (80)-35\% & (23)-10\% & 228\\
 \bottomrule[0.3mm]

### 2016-01-17 OSS_2016/paper.tex
Writting the results and some extra info about the tool

@@
 % your contribution title if the original one is too long
-\institute{\texttt{gerope@libresoft.es}, \texttt{jgb@gsyc.es},\texttt{grex@gsyc.es}
+\institute{\texttt{gerope@libresoft.es},\texttt{jgb@gsyc.es},\texttt{grex@gsyc.es}
 \and GSyC/LibreSoft, Universidad Rey Juan Carlos}
@@
 Identifying which of those issues are bug reports, is not a trivial task.
-When researchers want to conduct some study on the bug reports managed by a software development project, they need to first of all to perform this identification.
+When researchers want to conduct some study on the bug reports managed by a software development project, they need to first of all to perform this identification.\\
 
@@
 In the former case, researchers are usually not that experienced in the project, but they have at their disposal all the information produced, until the moment the issue was closed.
-This may include not only all comments and actions on the issue tracking system, but for examples, discusions about a fix in the code review system, or the final fixing patch in the source code management system.
+This may include not only all comments and actions on the issue tracking system, but for examples, discussions about a fix in the code review system, or the final fixing patch in the source code management system.
 Having all that information conveyed to the researchers in an easy, flexible and quick way accelerates and makes much more reliable their decision making process.
-This simplifies large scale manual analysis of issues (in the hundreds or thousands), helping researchers to ensure that they are really working with what they intend to work: bug reports.
+This simplifies large scale manual analysis of issues (in the hundreds or thousands), helping researchers to ensure that they are really working with what they intend to work: bug reports.\\
 
-	This paper presentes a tool designed exactly to solve this problem of providing the researcher with all the relevant information needed to decide if an issue corresponds to a bug report or not.
+This paper presents a tool designed exactly to solve this problem of providing the researcher with all the relevant information needed to decide if an issue corresponds to a bug report or not.
 The tool uses information extracted automatically from the project repositories, and offers a web-based interface which allows for collaboration, traceability and transparency of the identification of bug reports, making the process easier, faster, and more reliable.
@@
 Issue-tracking systems help solving these bugs, but their problem is the difficulty of distinguish the bug reports from other that are not bugs.
-These systems provide an interface to manage reports of maintenance activities where developers can report issues describing bug reports, features or optimizations.
+These systems provide an interface to manage reports of maintenance activities where developers can report issues describing bug reports, features or code optimizations.
 During the bug triage process it is difficult to distinguish bug reports from other issues; a study describes that two of five issues are misclassified~\cite{Herzig}.
@@
 
-In this paper, we present a tool to display all the data necessary to the developers to decide whether the issue is a bug report or not.
-The developers have the best available knowledge of their system, therefore the tool will help them choosing only bug reports to be analyzed in the bug-triage process removing any bias induced by non bug reports.
+In this paper, we present a tool to display all the data necessary to the developers who will decide whether the issue is a bug report or not.
+The developers have the best available knowledge of their system, therefore the tool will help them choosing only bug reports, removing any bias induced by non bug reports.
 
@@
 The tool works in the browser, displaying the main characteristics to distinguish bug report from others.
-Developers will be responsible to classify the tickets as bug report or not, could explain his decisions in each ticket.
+Developers will be responsible to classify the tickets as bug report or not, could explain their decissions in each ticket.
 
@@
 
-This project works with Launchpad as issue-tracking system and Gerrit as code review system.
-The image \ref{fig:1} presents the architecture used in the tool, which has been developed with JavaScript, Node, JQuery and HTML5 technologies.
-The server side works making queries to the API of Gerrit an Launchpad, and the client side is where the user can see the information displayed.
-The client side interacts with the server through events.
-Both sides share the information required using JSON files.
+This tool works with Launchpad as issue-tracking system and Gerrit as code review system.
+The image \ref{fig:1} presents the architecture used, which has been developed with JavaScript, Node, JQuery and HTML5 technologies.
+The server side works making queries to the API of Gerrit an Launchpad, and the client side is where the user can see the information displayed, and interacts with the server through events.
+Both sides share the information required using JSON files and use their own REST API.
 Furthermore, to integrate some functionalities from GitHub, we use a third-party application between GitHub and the browser.
@@
 
-The left side in the image \ref{fig:2}, shows the information related with the ticket in Launchpad and its correspondent fix-commit in Gerrit.
-Some information displayed link with the original pages in Launchpad and Gerrit, thereby the  developers have at their disposal extra information such as the comments that other developers have done.
+The left side in the image \ref{fig:2}, shows the information related with the ticket in Launchpad and its correspondent review in Gerrit.
+Some information displayed link with the original webpages in Launchpad and Gerrit, thereby the developers have at their disposal extra information such as the comments that other developers have done.
 Could tracking the history since the ticket opens until the commit fixed the ticket.
@@
 
-The tool allow carry out a double bind analysis, due to the data is saved in GitHub user's account.
-In order that, the user can only see and modify their own data saved.
+The tool allow carry out a double bind analysis, due to the data is saved in a file in GitHub user's account.
 GitHub is a control version system in which we have access to the whole information of each commit submitted by the developer.
 Thus, saving the data in GitHub, we could measure the time that each developer spend in the analysis, which tickets were more difficult to analyze and other statistics that can help us understanding the current problem of issues misclassification.
+
+\begin{figure}
+\centering
+\includegraphics[height=15cm]{index2.png}
+\caption{Screenshot of Analyze Tab}
+\label{fig:2}       % Give a unique label
+\end{figure}
+
+The webpage provide us different functionalities depend on in which tab we are, next we explain these functionalities.
+\begin{enumerate}
+  \item Tab Repository: In this tab we choose which repository of OpenStack we want analyze.
+Currently the tool supports the four principal repositories: Cinder, Nova, Neutron and Horizon, in which there is more activity.
+  \item Tab Analyze: Is the Tab showed in \ref{fig:2} where the user select/insert an identifyer of a ticket and analyze with all the data displayed if the ticket are a bug report or not.
+  \item Tab Statistics: This tab collects the data saved in the user's repository in GitHub after analyze each ticket, and displays a table with the number of tickets classified as \textit{Bug Report},\textit{Not Bug Report} and \textit{Undecided} in the repository and from each developer involved in the analysis, which name has to be selected previously.
+  \item Tab Modify: In this tab, the user can see all his data saved in the GitHub repository and modify the content of the file that he wants, in case of have inserted a mistake during the analysis.
+\end{enumerate}
 
@@
 Anyone can use it regardless of have GitHub account or not.
-But, they only can save and modify their data, in addition, one of the requirements to save and modify data is create a new repository with the same name that the repository of OpenStack you want to analyze.
+But, the ones with GitHub account are the only ones that can save and modify their data, in addition, one of the requirements to save and modify data is create a new repository with the same name that the repository of OpenStack which you want to analyze.
 
-\begin{figure}
-\centering
-\includegraphics[height=10cm]{index2.png}
-\caption{Screenshot of Index}
-\label{fig:2}       % Give a unique label
-\end{figure}
+%\section{Validation Study}
+%\label{sec:3}
 
-\section{Validation Study}
-\label{sec:3}
-
-OpenStack was particularly of interest because of its highest scope and heterogeneous nature with hundreds of developers contributing, furthermore due to its short life, only 5 years, all history is saved and available in a version control system.
+%OpenStack was particularly of interest because of its highest scope and heterogeneous nature with hundreds of developers contributing, furthermore due to its short life, only 5 years, all history is saved and available in a version control system.
 The issues are called tickets in OpenStack and available in the Launchpad, a web interface of ticket tracking system, classifying them as bug report or not.
 
-We use the tool to analyze 500 randomly tickets from the four principal repositories in OpenStack.
+%We use the tool to analyze 500 randomly tickets from the four principal repositories in OpenStack.
 This tickets could be tagged as either "Fix Commited" or "Fix Released", to be able to localize the patch implemented into de source code in the version repository.
@@
 
-The parameters analyzed for each ticket were the title and the description of the report and the description of the fix commit.
+%The parameters analyzed for each ticket were the title and the description of the report and the description of the fix commit.
 Also, the code changes if neither the descriptions and the comments clarified the underlying ticket.
 Each ticket was then categorized into one of three following groups.
-\begin{enumerate}
-  \item The ticket describes a bug report.
-  \item The ticket describes a feature, an optimization code, changes in test files or other not bug reports.
-  \item The ticket presents a vague description and cannot be classified without doubts.
-\end{enumerate}
+%\begin{enumerate}
+%  \item The ticket describes a bug report.
+%  \item The ticket describes a feature, an optimization code, changes in test files or other not bug reports.
+%  \item The ticket presents a vague description and cannot be classified without doubts.
+%\end{enumerate}
 
-Henceforth, we will refer to Group 1 as \textit{Bug Report}, Group 2 as \textit{not Bug Report} and Group 3 as \textit{Undecided}.
+%Henceforth, we will refer to Group 1 as \textit{Bug Report}, Group 2 as \textit{not Bug Report} and Group 3 as \textit{Undecided}.
 
-To validate the tool three different developers analyzed tickets belongs to the four main repositories.
-The developers analyzed more than three hundred tickets to can probe than the tool work as them expected, clasifiying the tickets into one of the three groups and corroborating that the issues reports present misclassification as ~\cite{Herzig} mencioned.
+%To validate the tool three different developers analyzed tickets belongs to the four main repositories.
+The developers analyzed more than four hundred tickets to can probe than the tool work as them expected, clasifiying the tickets into one of the three groups and corroborating that the issues reports present misclassification as ~\cite{Herzig} mencioned.
 
@@
 \label{sec:4}
-We have manually analyzed 500 tickets with support of the present tool. The table ~\ref{tab:1} show the statistics of each developer after analyzed the tickets.
 
+We have manually analyzed 459 different tickets with support of the present tool, 125 from Cinder, 125 fron Nova, 125 from Horizon and 84 from Neutron.
+The table ~\ref{tab:1} show the percentage of each developer after analyzing the tickets, 417 tickets were analyzed by two different developers,
 \begin{table}[htb]
@@
   & Bug Report\kern 1pc & Not Bug Report\kern 1pc & Undecided\kern 1pc & Total \\\hline
-Developer 1 \kern 1pc & (180)-54\% & (114)-34\% & (40)-12\% & 334 \\
-Developer 2 \kern 1pc & (188)-76\% & (51)-21\% & (8)-3\% & 247\\
-Developer 3 \kern 1pc & (125)-55\% & (80)-35\% & (23)-10\% & 228\\
+Developer 1 \kern 1pc & (184) 55\% & (115) 34\% & (35) 11\% & 334 \\
+Developer 2 \kern 1pc & (188) 76\% & (54) 22 \% & (7) 3\% & 249 \\
+Developer 3 \kern 1pc & (188) 56\% & (116) 35\% & (30) 9\% & 334 \\
 \bottomrule[0.3mm]
@@
 
-In the analysis, some of the tickets present a double bind review process, obtaining that each tickets was analyzed by two developers.
-The table ~\ref{tab:2} show the number of tickets analized with double bind review and the number tickets analized with only one review, as well as the percentaje of concordance obtained with the double bind.
+The percentages between Developer 1 and Developer 3 are really similar, whereas the Developer 2 has identifyed more Bug Reports in his analysis.
+But, the three results support the missclassification present in bug tracking systems.
+Futhermore, according to ~\cite{Herzig}'s work, approximately two of five issues are misclassified in the analysis of Developer 1 and Developer 3.
+
+Focusing in the concordance between developers analyzing the same ticket, 417 tickets present a double bind review process, obtaining that each tickets was analyzed by two developers.
+The table ~\ref{tab:2} show the percentaje of concordance between developers in each repository after the analysis of the tickets.
+Some repositories do not present double bind between two of developers.
 
@@
 \begin{center} {\footnotesize
-\caption{ Classification statistics of each developer}
+\caption{ Concordance between each developer in each repository}
 \label{tab:2}
@@
 \toprule[0.3mm]%{\smallskip}
-  & Nova \kern 1pc & Cinder \kern 1pc & Horizon \kern 1pc & Neutron \kern 1pc & Total\\\hline
-One revision \kern 1pc & --  & -- & -- & -- & -- \\
-Double Bind  \kern 1pc & -- & -- & -- & -- & --\\
-Concordance\\
-(only in double bind) \kern 1pc & --\% & --\% & --\% & --\% & --\\
+  & Nova\kern 1pc & Cinder\kern 1pc & Horizon\kern 1pc & Neutron\kern 1pc & Total\\\hline
+D1 and D2  \kern 1pc & (44/63) 70\%\kern 1pc & (40/52) 77\%\kern 1pc & (37/62) 60\%\kern 1pc & - \kern 1pc& 68\% \\
+D1 and D3  \kern 1pc &  -\kern 1pc & (46/63) 73\%\kern 1pc & (48/63) 76\%\kern 1pc & (26/42) 62\%\kern 1pc & 71 \% \\
+D2 and D3  \kern 1pc & (41/62) 66\%\kern 1pc & (10/10) 100\%\kern 1pc  & - \kern 1pc& -\kern 1pc  &  71\% \\
 \bottomrule[0.3mm]
@@
 
-%(should we corroborate that the statistics are similar with the previous study where only 100 tickets were analyze?\\
-%results with 100 tickets: (63\%) have been considered as Bug Report, (21\%) as Not Bug Report, and (16\%) as Undecided) )
-% Developer 1: 334 tickets
-% H--Ne--C--No
-% 64+50+31+35 --> 180 -->(53.89%)
-% 45+26+24+19 --> 114 -->(34.13\%)
-% 16+7+8+9 --> 40 --> (11.98\%)
-
 %\section{Discussion}
@@
 %\begin{enumerate}
-%\item Should they discuss after their analysis to reach a better classification?
-%\item Does the bug report only the same ticket classified as Bug report for all the developers?
+%\item Should they discuss after their analysis to reach a better classification?, Should the tool provide this?
+%\item Does the Bug report only the same ticket classified as Bug report for all the developers?
 %\end{enumerate}
 
-\subsection{Future Work}
-\label{sec:5.1}
+%\subsection{Future Work}
+%\label{sec:5.1}
 
-We would like know what grade of responsibility, none or totally, practice the previous commit in the seeding of a bug in OpenStack, considering that currently exists an implicit assumption: the line that contains the error was caused by the immediately previous commit\cite{Sliwerski}.
+%We would like know what grade of responsibility, none or totally, practice the previous commit in the seeding of a bug in OpenStack, considering that currently exists an implicit assumption: the line that contains the error was caused by the immediately previous commit\cite{Sliwerski}.
 The accuracy in our results depends on the quality of the data, thus we should focus only on bug reports discarding the other issues.
 
-The next step in the tool is implement the part in where we analyzed the previous commit, displaying the code after and before the bug fixed and after and before the bug-introduction to determinate if the previous commit is responsible or not.
+%The next step in the tool is implement the part in where we analyzed the previous commit, displaying the code after and before the bug fixed and after and before the bug-introduction to determinate if the previous commit is responsible or not.
 

### 2016-03-03 OSS_2016/paper.tex
aspell

@@
 The job for researchers here is very different from the bug triaging that developers do.
-In the latter case, people with a lot of experience in the project make a decission based on the information available at that time (maybe just a short comment by some user), asking if needed for more details.
+In the latter case, people with a lot of experience in the project make a decision based on the information available at that time (maybe just a short comment by some user), asking if needed for more details.
 In the former case, researchers are usually not that experienced in the project, but they have at their disposal all the information produced, until the moment the issue was closed.
@@
 The tool works in the browser, displaying the main characteristics to distinguish bug report from others.
-Developers will be responsible to classify the tickets as bug report or not, could explain their decissions in each ticket.
+Developers will be responsible to classify the tickets as bug report or not, could explain their decisions in each ticket.
 
@@
 The left side in the image \ref{fig:2}, shows the information related with the ticket in Launchpad and its correspondent review in Gerrit.
-Some information displayed link with the original webpages in Launchpad and Gerrit, thereby the developers have at their disposal extra information such as the comments that other developers have done.
+Some information displayed link with the original web pages in Launchpad and Gerrit, thereby the developers have at their disposal extra information such as the comments that other developers have done.
 Could tracking the history since the ticket opens until the commit fixed the ticket.
@@
 
-The webpage provide us different functionalities depend on in which tab we are, next we explain these functionalities.
+The web page provide us different functionalities depend on in which tab we are, next we explain these functionalities.
 \begin{enumerate}
@@
 Currently the tool supports the four principal repositories: Cinder, Nova, Neutron and Horizon, in which there is more activity.
-  \item Tab Analyze: Is the Tab showed in \ref{fig:2} where the user select/insert an identifyer of a ticket and analyze with all the data displayed if the ticket are a bug report or not.
+  \item Tab Analyze: Is the Tab showed in \ref{fig:2} where the user select/insert an identifier of a ticket and analyze with all the data displayed if the ticket are a bug report or not.
   \item Tab Statistics: This tab collects the data saved in the user's repository in GitHub after analyze each ticket, and displays a table with the number of tickets classified as \textit{Bug Report},\textit{Not Bug Report} and \textit{Undecided} in the repository and from each developer involved in the analysis, which name has to be selected previously.
@@
 We continue developing the tool but an initial version is available\footnote{\url{bugtracking.libresoft.es}}, as well as a demonstration video\footnote{\url{https://www.youtube.com/watch?v=q0-TIvL4mqc&feature=youtu.be}}.
-It presents a licence type GPL 0 (General Public License) and you can find the code in my GitHub account\footnote{\url{https://github.com/Gemarodri/BugTracking}}.
+It presents a license type GPL 0 (General Public License) and you can find the code in my GitHub account\footnote{\url{https://github.com/Gemarodri/BugTracking}}.
 Anyone can use it regardless of have GitHub account or not.
@@
 %To validate the tool three different developers analyzed tickets belongs to the four main repositories.
-The developers analyzed more than four hundred tickets to can probe than the tool work as them expected, clasifiying the tickets into one of the three groups and corroborating that the issues reports present misclassification as ~\cite{Herzig} mencioned.
+The developers analyzed more than four hundred tickets to can probe than the tool work as them expected, classifying the tickets into one of the three groups and corroborating that the issues reports present misclassification as ~\cite{Herzig} mentioned.
 
@@
 %Each developer analyzed 167 tickets plus the half tickets of his teammates.
-%Only at the end, they disscused the classification conflicts to reach an agreement.
+%Only at the end, they discussed the classification conflicts to reach an agreement.
 
@@
 
-We have manually analyzed 459 different tickets with support of the present tool, 125 from Cinder, 125 fron Nova, 125 from Horizon and 84 from Neutron.
+We have manually analyzed 459 different tickets with support of the present tool, 125 from Cinder, 125 from Nova, 125 from Horizon and 84 from Neutron.
 The table ~\ref{tab:1} show the percentage of each developer after analyzing the tickets, 417 tickets were analyzed by two different developers,
@@
 
-The percentages between Developer 1 and Developer 3 are really similar, whereas the Developer 2 has identifyed more Bug Reports in his analysis.
-But, the three results support the missclassification present in bug tracking systems.
-Futhermore, according to ~\cite{Herzig}'s work, approximately two of five issues are misclassified in the analysis of Developer 1 and Developer 3.
+The percentages between Developer 1 and Developer 3 are really similar, whereas the Developer 2 has identified more Bug Reports in his analysis.
+But, the three results support the misclassification present in bug tracking systems.
+Furthermore, according to ~\cite{Herzig}'s work, approximately two of five issues are misclassified in the analysis of Developer 1 and Developer 3.
 
 Focusing in the concordance between developers analyzing the same ticket, 417 tickets present a double bind review process, obtaining that each tickets was analyzed by two developers.
-The table ~\ref{tab:2} show the percentaje of concordance between developers in each repository after the analysis of the tickets.
+The table ~\ref{tab:2} show the percentage of concordance between developers in each repository after the analysis of the tickets.
 Some repositories do not present double bind between two of developers.
@@
 \end{table}
+
+The table ~\ref{tab:2} shows that the concordance of the developers is high but, also demonstrate the difficulty to classify tickets as bug report or as not bug report, because each developer can have different ideas about a specific ticket.
+The concordance between the developers could be higer if they were expert in the project.
+
 All the data is available in the repositories of github's account of the developers \footnote{\url{https://github.com/Gemarodri}}\footnote{\url{https://github.com/ddalipaj}}\footnote{\url{https://github.com/nellysek}}, these repositories has the same name that the projects analyzed in OpenStack.
@@
 
-%\subsection{Future Work}
-%\label{sec:5.1}
+\subsection{Future Work}
+\label{sec:5.1}
 
@@
 %The next step in the tool is implement the part in where we analyzed the previous commit, displaying the code after and before the bug fixed and after and before the bug-introduction to determinate if the previous commit is responsible or not.
+Future extensions of this tool includes extract information from others systems as Bugzilla or GitHub and study the misclassification in this projects.
+Also, display to users more information such as the status of the files affected in the fix commit after and before the bug-introducing.
+Furthermore, we would like to implement an auto classifier based on the semantic of the issue description and fix-commit description to help developers, showing a first idea about whereas the issue belongs to bug report or not, but the developer always has the last decision.
+After manually analyzing more than 400 tickets, we have seen clear cases of issues that were bug report, which have similar sentences in the description, so the automatic classification will allow developers to focus only on problematic issues, where it can be easily misclassification.
 

### 2016-03-03 OSS_2016/paper.tex
Changes proposedby Reviewers done!

@@
 In the former case, researchers are usually not that experienced in the project, but they have at their disposal all the information produced, until the moment the issue was closed.
-This may include not only all comments and actions on the issue tracking system, but for examples, discussions about a fix in the code review system, or the final fixing patch in the source code management system.
-Having all that information conveyed to the researchers in an easy, flexible and quick way accelerates and makes much more reliable their decision making process.
+This may include not only all comments and actions on the issue tracking system, but for example, discussions about a fix in the code review system, or the final fixing patch in the source code management system.
+Having all that information conveyed to the researchers in an easy, flexible and quick way accelerates and makes their decision process much more reliable.
 This simplifies large scale manual analysis of issues (in the hundreds or thousands), helping researchers to ensure that they are really working with what they intend to work: bug reports.\\
@@
 While a software system is being developed, software engineers use version repositories to produce and manage their code.
-Developers and tester report issues, which are stored in other repositories, known as issue-tracking system, where many kinds of issues can be found.
+Developers and testers report issues, which are stored in other repositories, known as issue-tracking systems, where many kinds of issues can be found.
 
-Issue-tracking systems help solving these bugs, but their problem is the difficulty of distinguish the bug reports from other that are not bugs.
+Issue-tracking systems help solving these bugs, but their problem is the difficulty of distinguishing the bug reports from other that are not bugs.
 These systems provide an interface to manage reports of maintenance activities where developers can report issues describing bug reports, features or code optimizations.
@@
 
-Linking a bug reports in a issue-tracking system and the corresponding fix-commit may be not a trivial task.
+Linking a bug report in a issue-tracking system and the corresponding fix-commit may not be a trivial task.
 Traditionally, the methods used in link recovery~\cite{Zimmermann, Thomas} are based on text patterns or the mining of key phrases.
 Unfortunately, these methods can include many false negatives causing bias in data~\cite{Bird, NguyenTH}.
-Therefore other methods, such as Mlink approach, have been developed to link bug report with fixes using features in the changed source files corresponding to commit logs in addition to the traditional textual features~\cite{Nguyen}.
-But all of them suppose that the issues are bug reports.
+Therefore other methods, such as the Mlink approach, have been developed to link bug report with fixes using features in the changed source files corresponding to commit logs in addition to the traditional textual features~\cite{Nguyen}.
+But all of this methods suppose that the issues are bug reports.
 
@@
 The developers have the best available knowledge of their system, therefore the tool will help them choosing only bug reports, removing any bias induced by non bug reports.
+(FIXME: (Review)the specific, original contribution of the proposal with respect to the state of the art is hard to recognise.)
+(FIXME:  It is a bit unclear what the more specific novelty with the tool.
+It is understood that it integrates several data sources and presents information to the researcher in the web interface, but does it operate under some more specific "philosophy" beyond being an tool that collects and integrates information at the same place?)
 
@@
 
-The tool works in the browser, displaying the main characteristics to distinguish bug report from others.
-Developers will be responsible to classify the tickets as bug report or not, could explain their decisions in each ticket.
+The tool works in a browser, displaying the main characteristics to distinguish bug report from others issues.
+Developers will be responsible to classify the issues from Launchpad, as bug report or not, and can thereby explain their decision for each issue.
+We will refer issue as ticket in this paper.
+(FIXME: The concept of a "ticket" should explaind first time it is mentioned (section 2))
 
@@
 Furthermore, to integrate some functionalities from GitHub, we use a third-party application between GitHub and the browser.
+(FIXME: it is a bit misleading to write that "image 1 presents the architecture used, which has been developed with JavaScript, Node, JQuery and HTML5 technologies.".
+It is probably not the architecture that has been developed using these technologies, but rather the software is based on the architecture presented in Figure 1.)
 
@@
 
-The left side in the image \ref{fig:2}, shows the information related with the ticket in Launchpad and its correspondent review in Gerrit.
-Some information displayed link with the original web pages in Launchpad and Gerrit, thereby the developers have at their disposal extra information such as the comments that other developers have done.
+The left side in the image \ref{fig:2}, shows the information related with the ticket in Launchpad and its corresponding review in Gerrit.
+(FIXME: The two subsequent sentences are very strange and hard to understand, should really be rephrased for clarity.)Some information displayed link with the original web pages in Launchpad and Gerrit, thereby the developers have at their disposal extra information such as the comments that other developers have done.
 Could tracking the history since the ticket opens until the commit fixed the ticket.
+( Is this way better?
+The developer can access to the Launchapd and Gerrit web pages through the links displayed in tool, thereby the developers can have extra information such as the comments that other developers have done in Launchpad or gerrit.
+This way, they could track the history of the ticket since it was open until the fix commit closed it.
+)
 
@@
 
-The tool allow carry out a double bind analysis, due to the data is saved in a file in GitHub user's account.
-GitHub is a control version system in which we have access to the whole information of each commit submitted by the developer.
-Thus, saving the data in GitHub, we could measure the time that each developer spend in the analysis, which tickets were more difficult to analyze and other statistics that can help us understanding the current problem of issues misclassification.
+The tool allow carry out a blind analysis, meaning that the analysis can be done by two or more developers in parallel since the data is saved in a file in GitHub user's account.
+GitHub is a control version system in which we have access to all information of each commit submitted by the developer.
+Thus, saving the data in GitHub, we could measure the time that each developer spends in the analysis, which tickets were more difficult to analyze and other statistics that can help us in understanding the current problem of issue misclassification.
 
@@
 
-The web page provide us different functionalities depend on in which tab we are, next we explain these functionalities.
+The web page provides different functionalities depending on in which tab we are. Next we explain these functionalities.
 \begin{enumerate}
-  \item Tab Repository: In this tab we choose which repository of OpenStack we want analyze.
-Currently the tool supports the four principal repositories: Cinder, Nova, Neutron and Horizon, in which there is more activity.
-  \item Tab Analyze: Is the Tab showed in \ref{fig:2} where the user select/insert an identifier of a ticket and analyze with all the data displayed if the ticket are a bug report or not.
-  \item Tab Statistics: This tab collects the data saved in the user's repository in GitHub after analyze each ticket, and displays a table with the number of tickets classified as \textit{Bug Report},\textit{Not Bug Report} and \textit{Undecided} in the repository and from each developer involved in the analysis, which name has to be selected previously.
+  \item Tab Repository: In this tab we choose which repository of OpenStack we want analyze. Currently the tool supports the four principal repositories: Cinder, Nova, Neutron and Horizon.
+  \item Tab Analyze: Is the Tab showed in Figure \ref{fig:2} where the user selects/inserts an identifier of a ticket and analyze with all the data displayed if the ticket is a bug report or not.
+  \item Tab Statistics: (FIXME: Language needs to be improved in remainder of this para.)This tab collects the data saved in the user's repository in GitHub after analyzing each ticket, and displays a table with the number of tickets classified as \textit{Bug Report},\textit{Not Bug Report} and \textit{Undecided} in the repository and from each developer involved in the analysis, which name has to be selected previously.
   \item Tab Modify: In this tab, the user can see all his data saved in the GitHub repository and modify the content of the file that he wants, in case of have inserted a mistake during the analysis.
@@
 We continue developing the tool but an initial version is available\footnote{\url{bugtracking.libresoft.es}}, as well as a demonstration video\footnote{\url{https://www.youtube.com/watch?v=q0-TIvL4mqc&feature=youtu.be}}.
-It presents a license type GPL 0 (General Public License) and you can find the code in my GitHub account\footnote{\url{https://github.com/Gemarodri/BugTracking}}.
-Anyone can use it regardless of have GitHub account or not.
-But, the ones with GitHub account are the only ones that can save and modify their data, in addition, one of the requirements to save and modify data is create a new repository with the same name that the repository of OpenStack which you want to analyze.
+It presents a license type GPL 0 (General Public License) and you can find the code at a GitHub page\footnote{\url{https://github.com/Gemarodri/BugTracking}}.
+Anyone can use it regardless of having GitHub account or not.
+(FIXME: Language needs to be improved in remainder of this para.) But, the ones with GitHub account are the only ones that can save and modify their data, in addition, one of the requirements to save and modify data is create a new repository with the same name that the repository of OpenStack which you want to analyze.
 
@@
 \label{sec:4}
-
+(FIXME: (Review)The test of the tool in section 3 involves three developers use of the tool in order to identify which issues are perceived as bug reports.
+My concern (or observation) is that it is not obvious that the results primarily are connected to the tool (but rather use of the tool), i.e.
+it could be claimed that the actual object(s) of study are the developers and how similarly the perceive issues being bug reports.
+What would the results look like if the tool was not used (but rather the data sources in isolation) or some other possible tool?
+I am not saying that the test/investigation is without value, but I think this should be discussed somewhere in the paper.
+)
 We have manually analyzed 459 different tickets with support of the present tool, 125 from Cinder, 125 from Nova, 125 from Horizon and 84 from Neutron.
-The table ~\ref{tab:1} show the percentage of each developer after analyzing the tickets, 417 tickets were analyzed by two different developers,
+Table ~\ref{tab:1} shows the percentage of issues classified as bug reports for the different developers,  (FIXME: Discuss (more clearly) why results are not reported in Table 2 for combinations "D1 and D3" for Nova, "D2 and D3" for Horizon, and "D1 and D2" \& "D2 and D3" for Neutron.)
 \begin{table}[htb]
@@
 
-Focusing in the concordance between developers analyzing the same ticket, 417 tickets present a double bind review process, obtaining that each tickets was analyzed by two developers.
-The table ~\ref{tab:2} show the percentage of concordance between developers in each repository after the analysis of the tickets.
+Focusing in the concordance between developers analyzing the same ticket, 417 tickets present a double bind review process, obtaining that each ticket was analyzed by two developers.
+Table ~\ref{tab:2} shows the percentage of concordance between developers in each repository after the analysis of the tickets.
 Some repositories do not present double bind between two of developers.
@@
 
-The table ~\ref{tab:2} shows that the concordance of the developers is high but, also demonstrate the difficulty to classify tickets as bug report or as not bug report, because each developer can have different ideas about a specific ticket.
-The concordance between the developers could be higer if they were expert in the project.
+Table ~\ref{tab:2} shows that the concordance of the developers is high but, also demonstrate the difficulty to classify tickets as bug report or as not bug report, because each developer can have different ideas about a specific ticket.
+The concordance between the developers could be higher if they were expert in the project.
 
-All the data is available in the repositories of github's account of the developers \footnote{\url{https://github.com/Gemarodri}}\footnote{\url{https://github.com/ddalipaj}}\footnote{\url{https://github.com/nellysek}}, these repositories has the same name that the projects analyzed in OpenStack.
+All the data iis available in the GitHub repositories of the developers \footnote{\url{https://github.com/Gemarodri}}\footnote{\url{https://github.com/ddalipaj}}\footnote{\url{https://github.com/nellysek}}, these repositories have the same name that the projects analyzed in OpenStack.
 
@@
 %The next step in the tool is implement the part in where we analyzed the previous commit, displaying the code after and before the bug fixed and after and before the bug-introduction to determinate if the previous commit is responsible or not.
+(FIXME: This section needs to be linguistically improved)
 Future extensions of this tool includes extract information from others systems as Bugzilla or GitHub and study the misclassification in this projects.
@@
 Furthermore, we would like to implement an auto classifier based on the semantic of the issue description and fix-commit description to help developers, showing a first idea about whereas the issue belongs to bug report or not, but the developer always has the last decision.
-After manually analyzing more than 400 tickets, we have seen clear cases of issues that were bug report, which have similar sentences in the description, so the automatic classification will allow developers to focus only on problematic issues, where it can be easily misclassification.
-
+After manually analyzing more than 400 tickets, we have seen clear cases of issues that were bug reports, which have similar sentences in the description, so the automatic classification will allow developers to focus only on problematic issues, which can be easily misclassified.
+\\
+(FIXME: it is understood that the current version of the tool is limited to Openstack projects/services and with the server operating against Launchpad and Gerrit.
+How well can the tool support other OSS projects through use of other kinds of repositories.
+This is hinted in 3.1 )\\
+(FIXME: There are three styles specifying authors in the reference list.
+Make it uniform and conformant with the Springer conference paper requirements.
+Do not use "et al." in reference list, list all authors.
+For references 1 and 2 the source is not specified.
+)
 \input{referenc}

### 2016-03-03 OSS_2016/referenc.tex
change references format

@@
 %Software Pioneers. Springer, Berlin Heidelberg New York
-\bibitem{Antoniol}Antoniol, Giuliano, et al. Is it a Bug or an Enhancement? A Text-based Approach to Classify Change Requests. 2008.
-\bibitem{Herzig}Herzig, Kim; Just, Sascha; Zeller, Andreas. It's not a Bug, it's a Feature: How Misclassification Impacts Bug Prediction. month, 2012.
-\bibitem{Sliwerski}J. Sliwerski, T. Zimmermann, and A. Zeller. When do
-changes induce fixes? ACM sigsoft software engineering
-notes, 30(4):1–5, 2005.
-\bibitem {Nguyen}Nguyen, Anh Tuan, et al.
-'Multi-layered approach for recovering links between bug reports and fixes.'' Proceedings of the ACM SIGSOFT 20th International Symposium on the Foundations of Software Engineering.
-ACM, 2012.
-\bibitem {Zimmermann}Zimmermann, Thomas; Premraj, Rahul; Zeller, Andreas.
+\bibitem{Antoniol}Antoniol, G., Ayari, K., Di Penta, M., Khomh, F., \& Gu\'eh\'eneuc, Y.
+G.
+(2008, October).
+Is it a bug or an enhancement?: a text-based approach to classify change requests.
+In Proceedings of the 2008 conference of the center for advanced studies on collaborative research: meeting of minds (p.
+23).
+ACM.
+\bibitem{Herzig}Herzig, K., Just, S., \& Zeller, A.
+(2013, May).
+It's not a bug, it's a feature: how misclassification impacts bug prediction.
+In Proceedings of the 2013 International Conference on Software Engineering (pp.
+392-401).
+IEEE Press.
+\bibitem{Sliwerski}J. Śliwerski, J., Zimmermann, T., \& Zeller, A. (2005, May). When do changes induce fixes?. In ACM sigsoft software engineering notes (Vol. 30, No. 4, pp. 1-5). ACM.
+\bibitem {Nguyen}Nguyen, A.
+T., Nguyen, T.
+T., Nguyen, H.
+A., \& Nguyen, T.
+N.
+(2012, November).
+Multi-layered approach for recovering links between bug reports and fixes.
+In Proceedings of the ACM SIGSOFT 20th International Symposium on the Foundations of Software Engineering (p.
+63).
+ACM.
+\bibitem {Zimmermann}Zimmermann, T., Premraj, R., \& Zeller, A.
+(2007, May).
 Predicting defects for eclipse.
-En Predictor Models in Software Engineering, 2007.
+In Predictor Models in Software Engineering, 2007.
 PROMISE'07: ICSE Workshops 2007.
-International Workshop on.
-IEEE, 2007.
-p.
-9-9.
-\bibitem{Thomas}Zimmermann, Thomas, and Peter Weißgerber. "Preprocessing CVS data for fine-grained analysis." Proceedings of the International Workshop on Mining Software Repositories. 2004.
+International Workshop on (pp.
+9-9).
+IEEE.
+\bibitem{Thomas}Zimmermann, T., \& Weißgerber, P.
+(2004, May).
+Preprocessing CVS data for fine-grained analysis.
+In Proceedings of the First International Workshop on Mining Software Repositories (pp.
+2-6).
+sn.
 \bibitem{Bird}Bird, C., Bachmann, A., Aune, E., Duffy, J., Bernstein, A., Filkov, V., \& Devanbu, P.

### 2016-03-07 OSS_2016/paper.tex
Some changes in the text according to the reviewers' suggestions

@@
 % your contribution title if the original one is too long
-\author{Gema Rodriguez\inst{1}, Jesus M. Gonzalez-Barahona\inst{1} \and Gregorio Robles\inst{1}}
+\author{Gema Rodr\'iguez-P\'erez\inst{1}, Jes\'us M. Gonzalez-Barahona\inst{2}, Gregorio Robles\inst{2},Dorealda Dalipaj\inst{1} \and Nelson Sekitoleko\inst{1}}
 %\and Name of Author\inst{2}}
@@
 % your contribution title if the original one is too long
-\institute{\texttt{gerope@libresoft.es},\texttt{jgb@gsyc.es},\texttt{grex@gsyc.es}
-\and GSyC/LibreSoft, Universidad Rey Juan Carlos}
+\institute{\texttt{\{gerope,ddalipaj,snelson}\}@libresoft.es, LibreSoft, University King Juan Carlos
+\and \texttt{\{jgb,grex\}}@gsyc.es, GSyC, University King Juan Carlos}
 %
@@
 Developers will be responsible to classify the issues from Launchpad, as bug report or not, and can thereby explain their decision for each issue.
-We will refer issue as ticket in this paper.
-(FIXME: The concept of a "ticket" should explaind first time it is mentioned (section 2))
+That issues is what will refer through this paper as ticket.
 
@@
 This tool works with Launchpad as issue-tracking system and Gerrit as code review system.
-The image \ref{fig:1} presents the architecture used, which has been developed with JavaScript, Node, JQuery and HTML5 technologies.
+The figure \ref{fig:1} presents the architecture used in the software, which has been developed with JavaScript, Node, JQuery and HTML5 technologies.
 The server side works making queries to the API of Gerrit an Launchpad, and the client side is where the user can see the information displayed, and interacts with the server through events.
@@
 
-The left side in the image \ref{fig:2}, shows the information related with the ticket in Launchpad and its corresponding review in Gerrit.
+The left side in the figure \ref{fig:2}, shows the information related with the ticket in Launchpad and its corresponding review in Gerrit.
 (FIXME: The two subsequent sentences are very strange and hard to understand, should really be rephrased for clarity.)Some information displayed link with the original web pages in Launchpad and Gerrit, thereby the developers have at their disposal extra information such as the comments that other developers have done.
@@
   \item Tab Analyze: Is the Tab showed in Figure \ref{fig:2} where the user selects/inserts an identifier of a ticket and analyze with all the data displayed if the ticket is a bug report or not.
-  \item Tab Statistics: (FIXME: Language needs to be improved in remainder of this para.)This tab collects the data saved in the user's repository in GitHub after analyzing each ticket, and displays a table with the number of tickets classified as \textit{Bug Report},\textit{Not Bug Report} and \textit{Undecided} in the repository and from each developer involved in the analysis, which name has to be selected previously.
-  \item Tab Modify: In this tab, the user can see all his data saved in the GitHub repository and modify the content of the file that he wants, in case of have inserted a mistake during the analysis.
+  \item Tab Statistics: This tab extracts the data already, analyzed by each developer involved in the analysis, from their users' accounts in GitHub.
+It analyzes this data to display a table with the number of tickets classified into the three categories; \textit{Bug Report},\textit{Not Bug Report} and \textit{Undecided}.
+To display the statistics of a developer, previously the name of developer has to be selected.
+  \item Tab Modify: In this tab, the user can see the data saved in his GitHub repository and modify the content of the file that he wants, in case of have inserted a mistake during the analysis.
 \end{enumerate}
@@
 Anyone can use it regardless of having GitHub account or not.
-(FIXME: Language needs to be improved in remainder of this para.) But, the ones with GitHub account are the only ones that can save and modify their data, in addition, one of the requirements to save and modify data is create a new repository with the same name that the repository of OpenStack which you want to analyze.
+(FIXME: Language needs to be improved in remainder of this para.) But, only the ones with GitHub account can use the GitHub available functionalities; saved the data analyzed, see the statistics and modified the data saved.
+The one requirement is open a repository in GitHub with the same name that the project you want to analyze in OpenStack.
 
@@
 We have manually analyzed 459 different tickets with support of the present tool, 125 from Cinder, 125 from Nova, 125 from Horizon and 84 from Neutron.
-Table ~\ref{tab:1} shows the percentage of issues classified as bug reports for the different developers,  (FIXME: Discuss (more clearly) why results are not reported in Table 2 for combinations "D1 and D3" for Nova, "D2 and D3" for Horizon, and "D1 and D2" \& "D2 and D3" for Neutron.)
+All the tickets have been analyzed by two of the three developers and the Table ~\ref{tab:1} shows the percentage of tickets classified as bug reports for the different developers.
+These results don't report for some combinations of developers because of  in some projects, only a developer analyzed all the tickets and the two remaining analyzed the half of these tickets each one.
+(FIXME: Discuss (more clearly) why results are not reported in Table 2 for combinations "D1 and D3" for Nova, "D2 and D3" for Horizon, and "D1 and D2" \& "D2 and D3" for Neutron.)
 \begin{table}[htb]
@@
 (FIXME: This section needs to be linguistically improved)
-Future extensions of this tool includes extract information from others systems as Bugzilla or GitHub and study the misclassification in this projects.
-Also, display to users more information such as the status of the files affected in the fix commit after and before the bug-introducing.
-Furthermore, we would like to implement an auto classifier based on the semantic of the issue description and fix-commit description to help developers, showing a first idea about whereas the issue belongs to bug report or not, but the developer always has the last decision.
+The current tool is limited to OpenStack projects due to we are carrying out an empirical study which based on these data, but future extensions of this tool includes extract issues from others systems as Bugzilla or GitHub to study the misclassification in the OSS projects which use these systems.
+Also, display to users more information such as the code of the files affected in the fix commit, and the code in the bug seeding moment.
+Furthermore, we would like to implement an auto classifier based on the semantic of the ticket description and fix-commit description to help developers in the analysis.
+This classifier will show a percentage of confident about whereas the ticket belongs to bug report or not, but the developer always has the last decision.
 After manually analyzing more than 400 tickets, we have seen clear cases of issues that were bug reports, which have similar sentences in the description, so the automatic classification will allow developers to focus only on problematic issues, which can be easily misclassified.
